### 2010-04-18 paper.tex
template inicial

%======================================================================
%----------------------------------------------------------------------
%               XX                           X
%                                            X
%               XX    XXX   XXX   XXX   XXX  X  XXXX
%                X   X   X X   X X   X X   X X X
%                X   XXXXX XXXXX XXXXX X     X  XXX
%                X   X     X     X     X   X X     X
%               XXX   XXX   XXX   XXX   XXX  X XXXX
%----------------------------------------------------------------------
%  	         SPECIFICATION FOR COMMON IEEE STYLES
%----------------------------------------------------------------------
%               Gregory L. Plett, Istv\'{a}n Koll\'{a}r.
%======================================================================
\documentclass[%
	%draft,
	%submission,
	%compressed,
	final,
	%
	%technote,
	%internal,
	%submitted,
	%inpress,
	reprint,
	%
	%titlepage,
	notitlepage,
	%anonymous,
	narroweqnarray,
	inline,
	twoside,
        invited,
	]{ieee}

\newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}

%\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
%\usepackage{ieeetc}	% if you want the "trans. comp." style
%\usepackage{ieeeimtc}	% if you want the IMTC conference style

% Use the `endfloat' package to move figures and tables to the end
% of the paper. Useful for `submission' mode.
%\usepackage {endfloat}

% Use the `times' package to use Helvetica and Times-Roman fonts
% instead of the standard Computer Modern fonts. Useful for the 
% IEEE Computer Society transactions.
%\usepackage{times}
% (Note: If you have the commercial package `mathtime,' (from 
% y&y (http://www.yandy.com), it is much better, but the `times' 
% package works too). So, if you have it...
%\usepackage {mathtime}

% for any plug-in code... insert it here. For example, the CDC style...
%\usepackage{ieeecdc}

\begin{document}

%----------------------------------------------------------------------
% Title Information, Abstract and Keywords
%----------------------------------------------------------------------
\title[Specification for Common IEEE Styles]{%
       Specification for Common IEEE Styles}

% format author this way for journal articles.
% MAKE SURE THERE ARE NO SPACES BEFORE A \member OR \authorinfo
% COMMAND (this also means `don't break the line before these
% commands).
\author[PLETT AND KOLL\'{A}R]{Gregory L. Plett\member{Student 
       Member},\authorinfo{G.\,L.\,Plett is with the Department of Electrical
       Engineering, Stanford University, Stanford, CA 94305--9510.
       Phone: $+$1\,650\,723--4769, e-mail: glp@simoon.stanford.edu}%
\and{}and Istv\'{a}n Koll\'{a}r\member{Fellow}\authorinfo{I.\
       Koll\'{a}r is with the Department of Measurement and Information
       Systems, Technical University of Budapest, 1521 Budapest, Hungary.
       Phone: $+$\,36\,1\,463--1774, fax: +\,36\,1\,463--4112, 
       e-mail: kollar@mmt.bme.hu}
}

% format author this way for conference proceedings
%\author[PLETT AND KOLL\'{A}R]{%
        %Gregory L. Plett\member{Student Member},\authorinfo{%
        %Department of Electrical Engineering,\\ 
        %Stanford University, Stanford, CA 94305-9510.\\
        %Phone: $+$1\,650\,723-4769, email: glp@simoon.stanford.edu}%
%\and{}and%
%\and{}Istv\'{a}n Koll\'{a}r\member{Fellow}\authorinfo{%
        %Department of Measurement and Instrument Engineering,\\ 
        %Technical University of Budapest, 1521 Budapest, Hungary.\\
        %Phone: $+$\,36\,1\,463-1774, fax: +\,36\,1\,463-4112, 
        %email: kollar@mmt.bme.hu}
%}

\journal{IEEE Trans.\ on Instrum.\ Meas.}
\titletext{, VOL.\ 46, NO.\ 6, DECEMBER\ 1997}
\ieeecopyright{0018--9456/97\$10.00 \copyright\ 1997 IEEE}
\lognumber{xxxxxxx}
\pubitemident{S 0018--9456(97)09426--6}
\loginfo{Manuscript received September 27, 1997.}
\firstpage{1217}

\confplacedate{Ottawa, Canada, May 19--21, 1997}

\maketitle

\begin{abstract} 
Our premise is that a researcher should be able to use his or her time
doing research, and not fighting with a text formatter. Modern
formatters have macro capability. If the proper macros are written,
the text formatting for all IEEE publications may be accomplished
automatically.  We propose that proponents of various text-processing
systems write macro packages for their own systems.  The scientific
community would benefit greatly.  One example is provided for users of
the \latexiie\ system. It is available at
\mbox{http://www--isl.stanford.edu/ieee/} or at the ftp site
\mbox{ftp://isl.stanford.edu/pub/ieee/}. A sim\-i\-lar macro package
is being developed for users of Microsoft Word, and can be found at
the world-wide-web addresses given in the Conclusion.
\end{abstract}

\begin{keywords}
Style file, \latexiie, Microsoft Word, IEEE Publications, Instrumentation
and Measurement Technology Conference, IMTC.
\end{keywords}

%----------------------------------------------------------------------
% SECTION I: Introduction
%----------------------------------------------------------------------
\section{Introduction}

\PARstart lololololol I'm amazed
submission of papers for publication. Depending on how the paper is to
be published, there are various typesetting formats for various
purposes, and it is frustrating and time-consuming to have to manually
format a paper to follow all of the guidelines.

A much better solution is to have the formatting done automatically.
Modern text processors and document-typesetting systems offer this
possibility by allowing user-defined macro packages or style files.
Sets of macros may be defined to automatically present a document in
any required format. Only one person, or a team of people, has to
write the macro package, and then the entire scientific community will
benefit. The only question is how to make such styles globally
available.

Each researcher has his or her own favorite text processor. We believe
that if the proponents of the main text processors (e.g., \latexiie,
Microsoft Word, Framemaker, WordPerfect, and so
forth\footnote{Microsoft Word is a trademark of Microsoft Corporation;
Frame\-maker is a trademark of Frame Technology Corporation;
WordPerfect is a trademark of Corel Corporation.}) cooperate, such
macro packages could be created. This would spare a lot of work for
both the authors and the editors of the paper.  By invoking different
macros, the author could immediately transform the style of a document
from a draft manuscript into a final camera-ready format, and so
forth, without the need for manual formatting.  In this document we
summarize our expectations for such macro packages, and introduce a
candidate solution for the \latexiie\ typesetting system. This
package, which we call \texttt{ieee.cls}, replaces both the old
\texttt{IEEEtran.sty} by Murray and Balemi, and the updated
\texttt{IEEEtran.cls} by N\"{u}chter. A similar solution is currently
being written for users of Microsoft Word.

%----------------------------------------------------------------------
% SECTION II: The Document Life-Cycle
%----------------------------------------------------------------------
\section{The Document Life-Cycle}

Each document to be published, regardless of whether it is destined to
be a journal article or a conference paper, goes through a certain
life-cycle. At each stage of the life-cycle, there are different
formatting needs. This may be summarized as follows:
\begin{description}
\item[Draft:] The first stage in the life-cycle is the draft stage.
    This is when the author is initially writing and editing the 
    manuscript. The formatting of the document should help the author 
    with this task. For example, the main text should be
    double-spaced, the margins should be wide enough to allow written
    comments, and a date-and-time stamp should be placed on each page to 
    help with version control.
\item[Internal Review:] After the draft version is finalized,
    the next stage in the life-cycle might be to give the paper
    to one or more colleagues for review. This stage is an internal review
    process, as opposed to the formal review done upon submission
    to the IEEE (see the next stage). Suggestions and 
    criticism at this stage can very much improve the quality of the 
    paper and can save much time in getting the paper 
    published. The formatting for an internal review is fairly flexible. 
    One requirement is that the paper contain a phrase to the effect that
    the document is preliminary and should not be circulated without
    permission of the author(s).  This can appear in the header or footer of
    the paper, for example.
\item[Submission for Review:] The next stage in the life-cycle is to 
    submit the paper to the IEEE for formal review by anonymous reviewers. 
    This review requires that the paper be formatted differently. In some 
    cases, the title of the paper, and especially the authors' names, 
    must be printed on a separate title page to ensure anonymity of the
    authors. Double-spacing of the main text is usually required, but not 
    time stamps, and so forth.
\item[Initial Distribution:] While the document is submitted or 
    ``in-press,'' it is desirable to be able to distribute the 
    preliminary version (e.g., on the world-wide-web) for the 
    benefit of other researchers. This, once again, will stipulate a 
    different format. The paper should indicate that it is
    ``submitted'' or ``in-press,'' and is not the final version, to 
    avoid confusion between the preliminary and eventual printed
    versions. The date is added on each page to further distinguish this
    from the final version.
\item[Final Form:] The IEEE uses its own software to format journal
    papers. The ``final'' mode of the proposed macro package will
    approximate the style of the published paper as closely as possible.
    This allows the researcher to estimate page lengths, and to 
    appropriately break equations and scale figures and tables. Perhaps 
    if a standard set of macro packages is developed, the IEEE may 
    eventually adopt it, and then the final-mode would be exactly 
    what is published!

    For IEEE conferences, the author may (and often must) provide a
    camera-ready formatted copy of the paper. In this case, the 
    ``final'' mode of the macro package produces \emph{exactly} what 
    is published.
\item[Submission for Publishing:] After the paper is accepted,
    and all the final corrections are made, it must be submitted for 
    publishing. To submit a paper to an IEEE conference, the format of 
    the paper is defined by the specifications used in the ``Final Form'' 
    stage of the life-cycle. However, if the paper is to be submitted
    to a journal, there are different formatting requirements for the
    submitted document.
\item[Final Distribution:] After the paper is published, it is
    beneficial to have an electronic version of the paper
    (e.g., for distribution on the world-wide-web). This final
    version should have correct page numbers, the IEEE copyright 
    information, the volume and issue number of the journal, and so forth.
\end{description}

Clearly, it is cumbersome to \emph{manually} re-format a paper for all
the stages of its life-cycle. We believe that a better solution is to
use macro packages for individual text-processing systems which can
automatically format a paper to certain specifications.  The format of
the paper is automatically changed by changing a single parameter.
This is not a dream! This has all been implemented for one
text-processing system (see Section~\ref{sec:latex}), and our hope is
that various readers and proponents of different text-formatting
systems will volunteer to implement these specifications for their
favorite text formatter. The entire research community will benefit
from these efforts.

%----------------------------------------------------------------------
% SECTION III: Specifications
%----------------------------------------------------------------------
\section{Specifications}

In this section, we give specifications which we feel must be
satisfied by a macro package to aid a researcher in preparing papers
for publication. We have followed this list very closely when writing
the example package \texttt{ieee.cls}.

%----------------------------------------------------------------------
\subsection{Draft Manuscript}

The draft mode is the format used while the author writes the manuscript. 
Its main characteristics are:
\begin{itemize}
\item Double spacing, single-column, and acceptably wide margins 
      to allow room for comments and proofreaders' marks.
\item A date-and-time stamp on each page to document the time of the
      printing for help with version control.
\item When figures belong to the manuscript, the author may switch
      among the basic options:
      \begin{enumerate}
      \item Figures are not printed, but the appropriate space is
            left in the manuscript.
      \item Figures are not printed, and the captions are
            included at the marked places with a small empty space.
      \item Figures are inserted into the manuscript.
      \item Figures are inserted one after the other at the end of the
            manuscript. 
      \item Figures are inserted, each on a separate page, at the end of the
            manuscript. 
      \end{enumerate}
\end{itemize}

%----------------------------------------------------------------------
\subsection{Internal Review}
The formatting requirements for an internal review are fairly loose.
The following are suggestions:
\begin{itemize}
\item The following text should be included:
      ``Preliminary version for evaluation: Please do not circulate 
      without the permission of the author(s)''
\item The figures should be included in the text, rather than at the
      end of the document. 
\item The text should be double-spaced, single-column, with wide enough 
      margins to allow for reviewers' corrections.
\item The date should be added to the header of each page. 
\end{itemize}

%----------------------------------------------------------------------
\subsection{Submission for IEEE Formal Review}
\label{sec:review}

The following are desirable for submission to the IEEE:
\begin{itemize}
\item The printout would obligatorily be double-spaced, single-column.  
\item The figures should be placed at the end of the paper and should
      be identical to the figures to be submitted for publication if
      the paper is accepted.
\item As some of the Transactions require a separation of the title
      page and the text to provide anonymity, this should be an
      option. 
\item The date of submission should be added on the title page 
      and the second page if a separate title page is generated.
\end{itemize}

%----------------------------------------------------------------------
\subsection{Transactions-like Printing for Evaluation and Length
Measurement}

This format should follow as precisely as practicable the format of the 
journal.

%----------------------------------------------------------------------
\subsection{Submission for Publication in a Journal}

This could be nearly identical to the case in
Section~\ref{sec:review}.  A mark should be placed in the text to show
about where each figure should go.  Figures may optionally be printed
at a larger scale to allow better photographic reproduction.  The date
of submission and possibly the editor's paper number should be added.

%----------------------------------------------------------------------
\subsection{Camera-ready Form for Conference Submission}

This is the only format that has a very strict and exactly defined
layout.  This layout will be defined separately for each conference,
on the basis of the its author's guide.

%----------------------------------------------------------------------
\subsection{Electronic Distribution (Initial and Final)}

A hardcopy or electronic version of the paper can be useful for
distribution during various stages in its life-cycle, but improper
information in this distributed form can lead to misunderstanding.
The format should provide some specific information.
\begin{itemize}
\item If the paper is currently submitted for review, the
      text ``Submitted to (journal or conference name) for
      publication,'' along with the date, should appear on the title
      page.  
\item If the paper has been accepted for publication, but is not
      yet printed, the text ``Accepted for publication by (journal or
      conference name), (in-press)'' should appear. 
\item In addition, for both of the above situations, the following text 
      should be included: ``Preliminary version: Please do not circulate 
      without the permission of the author(s).''
\item If the version is a reprint, the 
      text ``Reprinted from (journal or conference name)'' should be 
      included. Additionally, the page numbers should match the printed
      version, and the volume number, issue number and IEEE copyright 
      information should be included. 
\item To facilitate the paper's distribution on the world-wide-web,
      the height should be set 
      in a way that it can be printed both on A4 and U.S. letter-size paper. 
      A ``full'' A4 page cannot usually be printed in the United 
      States; the top lines will be missing. 
\end{itemize}
This form should allow a lot of freedom, such as one- or two-column
formatting, the inclusion of a cover page, and so on.

%----------------------------------------------------------------------
% SECTION IV: The LaTeX2e Class
%----------------------------------------------------------------------
\section{The \latexiie\ Class}
\label{sec:latex}

One text-formatting package in common use by researchers is the
\latexiie\ system~\cite{lamport}. Some of its features include a very
flexible macro capability, excellent formatting of mathematical
equations, seamless integration of text into graphics (using the
\texttt{psfrag.sty} package; see~\cite{goossens}), and affordable
price (it's free!).

Documents formatted with \latexiie\ must belong to a certain ``class.''
A class file is a set of macros which tells \latexiie\ how to format
the document. For example, the standard classes which are available
include an article class, a report class, a book class and a letter
class.

For the purpose of writing IEEE papers, we have developed a special
\latexiie\ ``class'' file. Users of \LaTeX\ probably know about
\texttt{IEEEtran.sty}, written by Murray and Balemi. This style was 
originally devised for evaluation and length measurement, but it is
close to meeting some of the above desires. It was written for the
now-obsolete \LaTeX 2.09, and has been modified for \latexiie\ by
N\"{u}chter. The latter, called \texttt{IEEEtran.cls}, may be found on
the IEEE world-wide-web site.  It implements much of the functionality
required for the ``Final Form'' stage of the document life-cycle. We
found it helpful as a starting point for this project. Our modified
version, called \texttt{ieee.cls}, satisfies all of the requirements
for each stage of the document life-cycle.

\subsection{Choosing the Paper's Style}

Documents written for \latexiie\ are written as plain text. The
\latexiie\ system converts the text into formatted pages. To tell
\latexiie\ how to format your document, certain commands need to be
entered into the text.

The \texttt{ieee.cls} class file makes this very easy.  The first line
of your document needs to specify a command of the form
\begin{verbatim}
  \documentclass[main-mode,
                 sub-mode,
                 misc-options]{ieee}
\end{verbatim}
where one ``main-mode'' is chosen from the following:
\begin{description}
\item[\texttt{draft}] Double-spaced, single-column, with date and time
     stamp.
\item[\texttt{submission}] Double-spaced, suitable for submitting the
     paper for review, or for submitting the paper for publishing.
\item[\texttt{compressed}] Same as ``submission,'' only single-spaced.
     This is suitable for archival, internal review, and for some 
     conference proceedings. 
\item[\texttt{final}] For IEEE journals, this mode approximates the
     journal's final form. For IEEE conferences, it formats
     the paper for a camera-ready printout.
\end{description}
The optional ``sub-mode'' is chosen from the following:
\begin{description}
\item[\texttt{internal}] The internal sub-mode can modify either the
    ``submission,'' 
    ``compressed,'' or ``final'' modes. It changes the header to notify 
    the reader that this is an evaluation preprint, and not to be
    distributed. 
\item[\texttt{submitted}] The submitted sub-mode can modify either the
    ``compressed'' or ``final'' modes. It changes the header to notify 
    the reader that this paper has been submitted to a certain journal 
    for publication, and that it is not to be distributed.
\item[\texttt{inpress}] The inpress sub-mode is similar to the submitted 
    sub-mode. It can modify either the ``compressed'' or ``final'' modes. 
    It changes the header to notify the 
    reader that this paper has been accepted by a certain journal for 
    publication, but that it has not yet been published. It specifies that 
    the paper is not to be distributed.
\item[\texttt{reprint}] The reprint sub-mode can modify only the ``final''
    mode. It changes the header to state that the paper is reprinted
    from a certain journal. It includes proper page numbers, IEEE
    copyright information and the IEEE log number.
\item[\texttt{technote}] When used in combination with ``final,''
    this sub-mode produces a two-column technical note.
\end{description}
The optional ``misc-options'' are chosen from the following:
\begin{description}
\item[\texttt{titlepage/notitlepage}] The titlepage option causes a
    separate title page to be produced. The notitlepage option 
    (default) does not produce a separate title page.
\item[\texttt{anonymous}] By default, all author information is included
    in the typeset paper.
    However, if the ``anonymous'' option is selected, author information
    is omitted from the paper (except for on the optional title page).
    Author information is omitted from the title line on the first
    page of the paper and from the header on all pages. The author's
    affiliation is omitted from the first page, and the author's 
    biography is also omitted. Anonymity may be required when
    submitting a paper for review.
\item[\texttt{invited}] If the paper is an invited paper (as this
    one is), the ``invited'' option prints \emph{(Invited Paper)} under the 
    authors' names on the first page of the paper.
\item[\texttt{9pt,10pt,11pt,12pt}] You may manually choose the paper's 
    type size.
    You should not need to do this since the ``correct'' size is
    automatically chosen. However, if you want, you may use these to
    change the type size of the main text. (``9pt'' is a bit of a hack
    to retain backward-compatibility.)
\item[\texttt{narroweqnarray}] This fixes a \LaTeX\ bug. The
    spacing around the ``='' sign in equation arrays is changed 
    to be the same as in displayed math.  
\item[\texttt{inline}] Compresses the horizontal spacing of in-text
    math equations. The authors think that the resulting equations
    look better than those normally produced by \latexiie.
\end{description}

Already we can see the power of \texttt{ieee.cls}. By changing a
single parameter in the first line of the document, the user can
change the entire format of the paper!

\subsection{Plug-Ins}

The main \texttt{ieee.cls} file specifies the formatting required for
a generic IEEE journal. However, some journals have their own
formatting particularities. For example, journals of the IEEE Signal
Processing Society have centered figure captions, and all other
journals have left-justified captions. Journals of the IEEE Computer
Society are formatted very differently from journals of all other
societies. Furthermore, each conference has its own style.

Rather than burdening the main \texttt{ieee.cls} file with the
definitions required for each journal, we have placed this task on
small ``plug-in'' files designed to work with \texttt{ieee.cls}. For
example, to format a document for the IEEE Transactions on Computers,
specify (after the \verb|\documentclass| command):
\begin{verbatim}
  \usepackage{ieeetc}
\end{verbatim}
Plug-in files are also used to format papers for conferences. The 
main mode of the paper should be ``final,'' and the 
conference style-file should be loaded. For example,
\begin{verbatim}
  \usepackage{ieeeimtc}
\end{verbatim}
specifies the style needed for the IEEE Instrumentation and
Measurement Technology Conference.

At the moment, plug-in files exist for almost all of the IEEE journals
(see the world-wide-web site mentioned in the Conclusion for
up-to-date information on which are supported), but only a few
conferences.  However, as the use of the \texttt{ieee.cls} package
increases, additional plug-ins will be created.

\subsection{More Definitions}

In addition to specification of the modes and options for the paper,
several more things need to be defined. For a regular IEEE journal
submission, define the journal name in the form
\begin{verbatim}
  \journal{IEEE Trans.\ Something}
\end{verbatim}
The journal name is used to compose the header for each page.  To add
any other information after the journal name, use \verb|\titletext|.
For example, to indicate the editor's manuscript number on a preprint,
you would type something like
\begin{verbatim}
  \titletext{, TN\#9999.}
\end{verbatim}

The date is printed in the header for certain combinations of document
options (e.g., for the submission mode). If you would like to pre-date
or post-date the article, type, for example,
\begin{verbatim}
  \renewcommand{\today}{July 4, 1776}
\end{verbatim}
To specify the IEEE copyright information on the first page of a
reprint, type
\begin{verbatim}
  \ieeecopyright{xxx--xxxx/97\$10.00 
    \copyright\ 1997 IEEE}
\end{verbatim}

Reprints also contain either an ``IEEE log number,'' a ``publisher
item identifier,'' or similar publishing information in the lower left
column on the first page. This can be entered as
\begin{verbatim}
  \lognumber{xxxxxxx}
\end{verbatim}
or
\begin{verbatim}
  \pubitemident{S xxxx--xxxx(97)xxxxx--x}
\end{verbatim}
or
\begin{verbatim}
  \loginfo{Manuscript received... }
\end{verbatim}
To specify the first page of a reprint of a paper beginning on page 
103 of a journal, you would type
\begin{verbatim}
  \firstpage{103}
\end{verbatim}
Finally, for a conference, the location and date are specified as, for
example,
\begin{verbatim}
  \confplacedate{Ottawa, Canada,  
                 May 19--21, 1997}
\end{verbatim}

\subsection{The Title Information}

The title-and-author information for a paper is entered as follows.
Define:
\begin{verbatim}
  \title[Short Title]{Title of paper}
  \author[Short Names]{First 
     Author\member{Student 
     Member}\authorinfo{Department 
     of Electrical Engineering\\ 
     Some University, Somewhere CA, 
     90210, USA}% 
  \and{}Second Author\member{Senior 
     Member}\authorinfo{Department 
     of Electrical Eng...}
  \and{}and Third 
     Author\member{Fellow}\authorinfo{...}
  }
\end{verbatim}

The \verb|\title| command may be used with or without the optional
first parameter specified within square brackets. If the parameter is
present, it is used as the title placed in the header on each page.
Otherwise, the actual title is used for both the header and the title
page.

Entering the author information is perhaps the most complicated part
of using this class. However, if the above template is used,
everything should work well. \emph{Note that some types of documents
ignore some of the author information.} For example, conference
proceedings and technical notes do not print IEEE membership
information.

As with the title command, there is an optional first parameter. If it
is specified, it is used as the authors' names for the header on every
odd page of an final-mode manuscript, for example.  Otherwise, no
author information is printed in the header.

The membership status of an author is entered via the 
\verb|\member| command, and the author's affiliation is specified
with the \verb|\authorinfo| command.  Note that the content required
in the \verb|\authorinfo| command tends to vary depending on whether
the paper is for a conference or for a journal. The number of manual
changes are small, and must be done by a human anyway. The example
given is for an IMTC conference.

Finally, note that the authors are separated by an \verb|\and|
command.  This command \emph{does not} insert the word ``and'' between
author names, but allows \latexiie\ to separate them intelligently. If
the word ``and'' is required before the final author's name, it must
be inserted additionally.

The title page or lines are actually produced by the command
\begin{verbatim}
  \maketitle
\end{verbatim}

\subsection{Document Preliminaries}

Users of the old \texttt{IEEEtran.sty} style will find the rest of the
instructions to be very familiar. The abstract is specified
\begin{verbatim}
  \begin{abstract} 
  ...
  \end{abstract}
\end{verbatim}
The keywords (or index terms) are specified via
\begin{verbatim}
  \begin{keywords}
  ...
  \end{keywords}
\end{verbatim}

\PARstart Many of the IEEE journals typeset the first character to be
two lines tall, as in this paragraph. Furthermore, the rest of the
first word is set in capital letters. This can be done using the
command

\unskip
\begin{verbatim}
  \PARstart Many of the IEEE...
\end{verbatim}

\PARstartCal Just for fun, and perhaps to make your draft submissions
look a little snazzy, you can also start the first paragraph with a
calligraphic character by, for example,

\unskip
\begin{verbatim}
  \PARstartCal Just for fun...
\end{verbatim}

The user should be aware that these larger characters may not be
available on all systems, and \latexiie\ may need to run
{\font\mf=logo10 \mf METAFONT} to generate them.

The main body of the paper is written according to standard \latexiie\
convention. We should also mention that, as with the package
\texttt{IEEEtran.cls}, theorems and proofs may be defined as in this
example: 
\begin{verbatim}
  \newtheorem{theorem}{Theorem}
  ...
  \begin{theorem}[Theorem name]
    Consider the system ...
  \end{theorem}
  \begin{proof}
    The proof is trivial.
  \end{proof}
\end{verbatim}

\subsection{The End of the Paper}

The references in the paper are formatted with {\sc Bib}\TeX\ via the
special IEEE {\sc Bib}\TeX\ style file \texttt{IEEEbib.bst}. This file
has not been modified by us, and may be found on the IEEE
world-wide-web server.  To use it, insert the following lines in your
paper where the references are to be placed:
\begin{verbatim}
  \bibliographystyle{IEEEbib}
  \bibliography{filename}
\end{verbatim}
where \texttt{\emph{filename.bib\/}} is the name of the
bibliography data\-base file comprising all your {\sc Bib}\TeX\ entries.
The \latexiie\ manual explains how to use {\sc Bib}\TeX\ and how to
create bibliography files.

Finally, regular journal papers should include the biographies of
their authors.  This may be done simply as shown in the following:
\begin{verbatim}
  \begin{biography}{Istv\'{a}n Koll\'{a}r} 
  (M'87--SM'93--F'97) was born...

  From September 1993 to June 1995, ... 
  \end{biography}
\end{verbatim}
An optional first parameter specifies the file that contains the 
author's ``photograph.''
\begin{verbatim}
  \begin{biography}[face.ps]{Gregory L. 
  Plett} (S'97) was born ...
  \end{biography}
\end{verbatim}
This can be especially useful for preprints and reprints of the
document.  If you do not specify this first parameter, a framed empty
box is printed; however, any file that is recognized by
\verb|\includegraphics| may be used.  The aspect ratio of the
photograph should be approximately 25 by 32.  If it is a few percent
away from the desired aspect ratio, the picture is re-sized
non-proportionally.  Otherwise, it is shrunk proportionally to fit the
space and is then placed, centered, in a box of the correct size; a
warning message ``Too wide/tall'' is printed.

Note that a single blank line in the biography environment causes
paragraph separation. But beware: Multiple blank lines in a row will
leave a larger vertical space between paragraphs.

%----------------------------------------------------------------------
% SECTION V: Putting it all Together
%----------------------------------------------------------------------
\section{Putting it all Together}

To be perfectly clear, Fig.~\ref{fig-example} summarizes the commands
necessary to format a document using the \texttt{ieee.cls} file. The
\latexiie\ source for this paper is also available at the
world-wide-web site mentioned in the Conclusion, furnishing a more
complete example.

\begin{figure}[htb]
\begin{center}\small
\begin{tabular}{|l|}\hline
\begin{minipage}{0.9\hsize}
\vspace{3mm}
{\small
\begin{verbatim}
\documentclass[final]{ieee}

\begin{document}

\title[Specification for ...]{%
   Specification for ...}

\author[PLETT AND KOLL\'{A}R]{%
   Gregory L. Plett\member{Student 
   Member},\authorinfo{G.\ L.\ 
   Plett is ...}
\and{}and Istv\'{a}n 
   Koll\'{a}r\member{Fellow}\authorinfo{I.\
   Koll\'{a}r is ...}
}

\journal{IEEE Transactions on ...}

\maketitle

\begin{abstract}
Our premise...
\end{abstract}

\begin{keywords}
Style file...
\end{keywords}

\section{Introduction}
\PARstart An important aspect of...

\bibliographystyle{IEEEbib}
\bibliography{bib-file}

\begin{biography}{Gregory L. Plett} (S'97)
...
\end{biography}

\end{document}
\end{verbatim}
}
\vspace{1mm}
\end{minipage} \\ \hline
\end{tabular}
\end{center}
\caption{Input used to produce this paper.}
\label{fig-example}
\end{figure}

\section{Figures}

Figures in the text require special attention. First, when submitting
a paper for printing, it is often required that the figures and tables
be at the end of the paper. This can be handled by the
\texttt{endfloat.sty} package, which is part of the standard \latexiie\
distribution.

The documentation for the ``endfloat'' package is somewhat daunting,
but all that should be required is to specify
\begin{verbatim}
  \usepackage{endfloat}
\end{verbatim}
before the \verb+\begin{document}+ command in the paper. The default 
options should work well.

Whether or not you use the \texttt{endfloat.sty} package, encapsulated
postscript (EPS) files may be included simply in the text by
\begin{verbatim}
  \includegraphics{figname.eps}
\end{verbatim}
Partial documentation for the \verb|\includegraphics| command is
available in the \latexiie\ user's guide~\cite{lamport,goossens}, and
complete documentation is available in \texttt{epslatex.ps}, included
in the standard distribution of \latexiie. The reader should note that
the new \verb|\includegraphics| command supersedes the older
style-packages \texttt{epsfig.sty} and \texttt{psfig.sty}, which are
no longer required.

The reader may also wish to investigate the very powerful
\texttt{psfrag.sty} package, which is again part of the
standard distribution. It allows one to change labels in EPS files to
use \LaTeX's fonts, and it produces a very polished looking paper.

\subsection{Figure Management with \protect{\tt\lowercase{ieeefig.sty}}}

Finally, we have developed another package to aid in figure
preparation. It is called \texttt{ieeefig.sty}, and is especially
suited for use with the \texttt{psfrag.sty} package.  It provides a
practical method to manage a large number of figures efficiently.  It
is designed to work with \texttt{ieee.cls}, but will also work with
all of the standard \latexiie\ classes (e.g., for writing reports,
writing books, or creating presentation transparencies).  The
\texttt{ieeefig.sty} package is loaded by specifying (after the
\verb|\documentclass| command)
\begin{verbatim}
  \usepackage[options]{ieeefig}
\end{verbatim}
The options will be discussed shortly.

To use the \texttt{ieeefig.sty} package, you must place each figure in
its own \latexiie\ file (e.g., \texttt{\emph{figname.tex}}). The file
\texttt{\emph{figname.tex}} contains all of the commands necessary to
produce the figure. These commands might include \verb|\psfrag|
commands to replace labels in an EPS file with \LaTeX\ formatted text,
and the command necessary to load the EPS file.

The figure is included in the text of the paper via the following
commands:
\begin{verbatim}
  \begin{figure}
    \figdef[dim]{figname}
    \caption{This figure...}
    \label{fig:figname}
  \end{figure}
\end{verbatim}
It is automatically centered in its column. (The optional argument in
square brackets, ``dim,'' is the vertical size of the figure. It
defines the amount of vertical space to be skipped if the ``blank''
option is used.)

Through separation of the figure-generating commands from the main
paper, the figure is portable and may be re-used in other papers,
reports or presentations. It also permits \texttt{ieeefig.sty} to
perform some useful tasks. These tasks are controlled either by the
options used when loading the style or by a series of commands. The
available options may be chosen from the following:
\begin{description}
\item[\texttt{draft}] Displays the filename \texttt{\emph{figname.tex\/}} in the
    margin. Also displays the height of the figure. In this way, you can
    determine the correct value of the optional argument ``dim'' of the 
    \verb|\figdef| command.
\item[\texttt{final}] Does not display the filename or height of the figure.
\item[\texttt{blank}] Instead of displaying figures, 
    \verb|\figdef| will leave a vertical space on the page.  The height of 
    the vertical space is specified by the optional argument ``dim'' of the 
    \verb|\figdef| command. By omitting figures, you will
    allow 
    \latexiie\ to compile your document more quickly. This option may also 
    be selected in the document by the command \verb|\draftfigstrue|.
\item[\texttt{noblank}] This is the complement of the 
    \texttt{blank} option. Figures are shown. This option may also be
    selected in the document via the command \verb|\draftfigsfalse|.
\item[\texttt{frame}] This option causes each figure to be surrounded
    by a box, which can help determine whether the bounding box 
    on an EPS file is correct. The bounding box often must be adjusted if the
    \texttt{psfrag.sty} package is being used and labels go outside the 
    boundary of the figure. If the bounding box is incorrect, the figure
    will not be centered properly, and the spacing before and after the 
    figure will be incorrect. To adjust the bounding box, see the
    \texttt{trim} command below. This option may also be selected in the
    document using the command \verb|\figframestrue|.
\item[\texttt{noframe}] Frames are not drawn around figures. This option
    may also be selected in the document through the command
    \verb|\framefigsfalse|.
\end{description}

If EPS files are being loaded in the \texttt{\emph{figname.tex\/}} file, they
should be loaded using the command
\begin{verbatim}
  \inserteps[trim=a b c d]{figname.eps}
\end{verbatim}
This command inserts the EPS file \texttt{\emph{figname.eps}} at the correct
scale. It also adjusts the bounding box by trimming off \texttt{\emph{a}}, 
\texttt{\emph{b}}, \texttt{\emph{c}}, and \texttt{\emph{d}} points from 
the left, bottom, right and top
edges of the figure, respectively. Negative trim amounts increase the
size of the bounding box. If any \verb|\psfrag| statements have been
made for this figure, they will take effect with this command.

Finally, to scale all EPS figures by a constant ``num'' use
\begin{verbatim}
  \setfigscale{num}
\end{verbatim}
This is very useful for specifying different scales for presentation
transparencies and for reports. If the \verb|\setfigscale| command is
in the main paper text, then it applies to all figures from that point
in the paper onward. If it is inside of an individual
\texttt{\textit{figname.tex\/}} file, then it applies only to that
figure.

%----------------------------------------------------------------------
% SECTION VI: Wish List
%----------------------------------------------------------------------
\section{Wish List for \protect{\tt\lowercase{ieee.cls}}}

The \latexiie\ class package, \texttt{ieee.cls}, used in conjunction
with the \texttt{endfloat.sty} and \texttt{ieeefig.sty} packages
provides nearly all the desired functionality of a package to format
IEEE papers.  Several things remain outstanding, however.

The biggest omission is that ``plug-ins'' exist for only a few
conferences.  We hope that researchers who have developed styles for
other IEEE conferences will modify their styles to fit within the
\texttt{ieee.cls} framework, and will then contribute their work to
the scientific community.

A more subtle issue is that none of the two-column modes balance the
columns on the last page of the paper. The standard package
\texttt{multicol.sty} may be able to help, but it apparently does not
allow single-column figures and tables. Perhaps some {\TeX}pert out
there can fix this. Right now, the only work-around is for the user to
manually insert a \verb|\newpage| at the appropriate place to try to
balance the columns on the last page of the paper. This is a poor
solution at best.

Finally, the multi-blank-line bug in the biography environment should
be fixed. Until it is, the work-around is to be careful to leave only
a single blank line between paragraphs.

%----------------------------------------------------------------------
% SECTION VII: Conclusions
%----------------------------------------------------------------------
\section{Conclusion}

We have outlined a specification for macro packages to aid an author
of papers for IEEE publications. Additionally, we have provided a
\latexiie\ class which accomplishes most of these goals. Users of other
text-formatting systems are encouraged to write similar macro packages
for the benefit of the research community. Anyone interested in this 
task should contact the second author via e-mail.

The \latexiie\ class, which was used as an example here,
is provided on an ``as-is'' basis at

\begin{verbatim}
  http://www-isl.stanford.edu/ieee/
\end{verbatim}

\noindent or at

\begin{verbatim}
  ftp://isl.stanford.edu/pub/ieee/
\end{verbatim}

\noindent Any bug report is welcome, especially if accompanied by the solution!
Reports should be made, via e-mail, to the first author.

A similar macro package is under development for users of Microsoft Word. 
It is available at

\begin{verbatim}
  http://www.ifm.liu.se/Meastech/Bjorn/IMTC.html
\end{verbatim}

\noindent At the present time, it is able to format papers for the IEEE
Instrumentation and Measurement Technology Conference. 
References to both packages can also be found on the IM Society page

\begin{verbatim}
  http://www.ieee.org/society/im/im.htm
\end{verbatim}

We hope that this paper sparks interest and imagination. We also hope
that the \latexiie\ and Microsoft Word classes save many researchers much work.

%----------------------------------------------------------------------
% The bibliography. This bibliography was generated using the following
% two lines:
%\bibliographystyle{IEEEbib}
%\bibliography{ieeecls}
% where, the contents of the ieeecls.bib file was:
%
%@book{lamport,
%        AUTHOR = "Leslie Lamport",
%         TITLE = "A Document Preparation System: {\LaTeX} User's Guide
%                  and Reference Manual",
%       EDITION = "Second",
%     PUBLISHER = "Addison-Wesley",
%       ADDRESS = "Reading, MA",
%          YEAR = 1994,
%          NOTE = "Be sure to get the updated version for \LaTeX2e!"
%}
%
%@book{goossens,
%        AUTHOR = "Michel Goossens and Frank Mittelbach and
%                  Alexander Samarin",
%         TITLE = "The {\LaTeX} Companion",
%     PUBLISHER = "Addison-Wesley",
%       ADDRESS = "Reading, MA",
%          YEAR = 1994,
%}
%
% The ieeecls.bbl file was manually included here to make the distribution
% of this paper easier. You need not do it for your own papers.

\begin{thebibliography}{1}

\bibitem{lamport}
Leslie Lamport,
\newblock {\em A Document Preparation System: {\LaTeX} User's Guide and
  Reference Manual},
\newblock Addison-Wesley, Reading, MA, 2nd edition, 1994.
\newblock Be sure to get the updated version for \latexiie!

\bibitem{goossens}
Michel Goossens, Frank Mittelbach, and Alexander Samarin,
\newblock {\em The {\LaTeX} Companion},
\newblock Addison-Wesley, Reading, MA, 1994.

\end{thebibliography}

%----------------------------------------------------------------------

\begin{biography}{Gregory L. Plett} 
(S'97) was born in Ottawa, ON, in 1968. He received the B.Eng.\ degree
in computer systems engineering with high distinction from Carleton
University, Ottawa, in 1990, and the M.S.\ degree in electrical
engineering from Stanford University, CA, in 1992.  He is currently a
Ph.D.\ candidate at Stanford University, where he is researching
aspects of adaptive control under the supervision of Professor Bernard
Widrow.
\end{biography}

\begin{biography}{Istv\'{a}n Koll\'{a}r} 
(M'87--SM'93--F'97) was born in Budapest, Hungary, in 1954. He graduated 
in electrical engineering from the Technical University of Budapest in 
1977 and in 1985 received the degree ``Candidate of Sciences'' (the 
equivalent of Ph.D.) from the Hungarian Academy of Sciences, and the 
degree dr.tech.\ from the Technical University of Budapest.

From September 1993 to June 1995, he was a Fulbright Scholar and
visiting associate professor in the Department of Electrical
Engineering, Stanford University. He is professor of electrical
engineering, Department of Measurement and Information Systems,
Technical University of Budapest. His research interests span the
areas of digital and analog signal processing, measurement theory, and
system identification. He has published about 50 scientific papers and
is coauthor of the book \emph{Technology of Electrical Measurements},
(L.\ Schnell, ed., Wiley, 1993). He authored the \emph{Frequency
Domain System Identification Toolbox} for Matlab.
\end{biography}

\end{document}

### 2010-04-25 paper.tex
template actualizado, borre cosas de mas

@@
 %======================================================================
-%----------------------------------------------------------------------
-%               XX                           X
-%                                            X
-%               XX    XXX   XXX   XXX   XXX  X  XXXX
-%                X   X   X X   X X   X X   X X X
-%                X   XXXXX XXXXX XXXXX X     X  XXX
-%                X   X     X     X     X   X X     X
-%               XXX   XXX   XXX   XXX   XXX  X XXXX
-%----------------------------------------------------------------------
-%  	         SPECIFICATION FOR COMMON IEEE STYLES
-%----------------------------------------------------------------------
-%               Gregory L. Plett, Istv\'{a}n Koll\'{a}r.
+% DVCS paper!
 %======================================================================
@@
 	%inpress,
-	reprint,
+	%reprint,
 	%
@@
 	twoside,
-        invited,
+        %invited,
 	]{ieee}
@@
 %----------------------------------------------------------------------
-\title[Specification for Common IEEE Styles]{%
-       Specification for Common IEEE Styles}
+\title[Investigation on GIT]{%
+       Investigation on GIT}
 
@@
 % commands).
-\author[PLETT AND KOLL\'{A}R]{Gregory L. Plett\member{Student 
-       Member},\authorinfo{G.\,L.\,Plett is with the Department of Electrical
-       Engineering, Stanford University, Stanford, CA 94305--9510.
-       Phone: $+$1\,650\,723--4769, e-mail: glp@simoon.stanford.edu}%
-\and{}and Istv\'{a}n Koll\'{a}r\member{Fellow}\authorinfo{I.\
-       Koll\'{a}r is with the Department of Measurement and Information
-       Systems, Technical University of Budapest, 1521 Budapest, Hungary.
-       Phone: $+$\,36\,1\,463--1774, fax: +\,36\,1\,463--4112, 
-       e-mail: kollar@mmt.bme.hu}
+\author[GRUPOAPIT]{Damian Alonso,%
+\and{} Bruno Bonnano
+\and{} Nicol\'{a}s Calligaro
+\and{}and Nicol\'{a}s Perez Santoro
 }
 
-% format author this way for conference proceedings
-%\author[PLETT AND KOLL\'{A}R]{%
-        %Gregory L. Plett\member{Student Member},\authorinfo{%
-        %Department of Electrical Engineering,\\ 
-        %Stanford University, Stanford, CA 94305-9510.\\
-        %Phone: $+$1\,650\,723-4769, email: glp@simoon.stanford.edu}%
-%\and{}and%
-%\and{}Istv\'{a}n Koll\'{a}r\member{Fellow}\authorinfo{%
-        %Department of Measurement and Instrument Engineering,\\ 
-        %Technical University of Budapest, 1521 Budapest, Hungary.\\
-        %Phone: $+$\,36\,1\,463-1774, fax: +\,36\,1\,463-4112, 
-        %email: kollar@mmt.bme.hu}
-%}
+\journal{Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires}
+%\titletext{, VOL.\ 46, NO.\ 6, DECEMBER\ 1997}
+%\ieeecopyright{0018--9456/97\$10.00 \copyright\ 1997 IEEE}
+%\lognumber{xxxxxxx}
+%\pubitemident{S 0018--9456(97)09426--6}
+%\loginfo{Manuscript received September 27, 1997.}
+\firstpage{1}
 
-\journal{IEEE Trans.\ on Instrum.\ Meas.}
-\titletext{, VOL.\ 46, NO.\ 6, DECEMBER\ 1997}
-\ieeecopyright{0018--9456/97\$10.00 \copyright\ 1997 IEEE}
-\lognumber{xxxxxxx}
-\pubitemident{S 0018--9456(97)09426--6}
-\loginfo{Manuscript received September 27, 1997.}
-\firstpage{1217}
-
-\confplacedate{Ottawa, Canada, May 19--21, 1997}
+\confplacedate{Buenos Aires, Argentina, April 18, 2010}
 
@@
 \begin{abstract} 
-Our premise is that a researcher should be able to use his or her time
-doing research, and not fighting with a text formatter. Modern
-formatters have macro capability. If the proper macros are written,
-the text formatting for all IEEE publications may be accomplished
-automatically.  We propose that proponents of various text-processing
-systems write macro packages for their own systems.  The scientific
-community would benefit greatly.  One example is provided for users of
-the \latexiie\ system. It is available at
-\mbox{http://www--isl.stanford.edu/ieee/} or at the ftp site
-\mbox{ftp://isl.stanford.edu/pub/ieee/}. A sim\-i\-lar macro package
-is being developed for users of Microsoft Word, and can be found at
-the world-wide-web addresses given in the Conclusion.
+Abstract to be done
 \end{abstract}
@@
 \begin{keywords}
-Style file, \latexiie, Microsoft Word, IEEE Publications, Instrumentation
-and Measurement Technology Conference, IMTC.
+to be done
 \end{keywords}
@@
 
-\PARstart lololololol I'm amazed
-submission of papers for publication. Depending on how the paper is to
-be published, there are various typesetting formats for various
-purposes, and it is frustrating and time-consuming to have to manually
-format a paper to follow all of the guidelines.
+\PARstart Vamos a contar cuando surgió esta tecnología y sus principales 
+exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
+similitudes con otros sistemas de versionado distribuidos como Mercurial. 
+Un poco se contará las diferencias fundamentales entre las herramientas de 
+versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
+pero no explicándolas.
 
-A much better solution is to have the formatting done automatically.
-Modern text processors and document-typesetting systems offer this
-possibility by allowing user-defined macro packages or style files.
-Sets of macros may be defined to automatically present a document in
-any required format. Only one person, or a team of people, has to
-write the macro package, and then the entire scientific community will
-benefit. The only question is how to make such styles globally
-available.
+La idea del paper sería contar las ventajas que puede 
+tener este esquema dentro de un ambiente enterprise de código cerrado, en contraste 
+a un ambiente open source donde el esquema distribuido tiene incluso más sentido.
 
-Each researcher has his or her own favorite text processor. We believe
-that if the proponents of the main text processors (e.g., \latexiie,
-Microsoft Word, Framemaker, WordPerfect, and so
-forth\footnote{Microsoft Word is a trademark of Microsoft Corporation;
-Frame\-maker is a trademark of Frame Technology Corporation;
-WordPerfect is a trademark of Corel Corporation.}) cooperate, such
-macro packages could be created. This would spare a lot of work for
-both the authors and the editors of the paper.  By invoking different
-macros, the author could immediately transform the style of a document
-from a draft manuscript into a final camera-ready format, and so
-forth, without the need for manual formatting.  In this document we
-summarize our expectations for such macro packages, and introduce a
-candidate solution for the \latexiie\ typesetting system. This
-package, which we call \texttt{ieee.cls}, replaces both the old
-\texttt{IEEEtran.sty} by Murray and Balemi, and the updated
-\texttt{IEEEtran.cls} by N\"{u}chter. A similar solution is currently
-being written for users of Microsoft Word.
+Ejemplo de cita \cite{linusgit}
 
 %----------------------------------------------------------------------
-% SECTION II: The Document Life-Cycle
+% SECTION II: Architecture
 %----------------------------------------------------------------------
-\section{The Document Life-Cycle}
+\section{Architecture}
 
-Each document to be published, regardless of whether it is destined to
-be a journal article or a conference paper, goes through a certain
-life-cycle. At each stage of the life-cycle, there are different
-formatting needs. This may be summarized as follows:
-\begin{description}
-\item[Draft:] The first stage in the life-cycle is the draft stage.
-    This is when the author is initially writing and editing the 
-    manuscript. The formatting of the document should help the author 
-    with this task. For example, the main text should be
-    double-spaced, the margins should be wide enough to allow written
-    comments, and a date-and-time stamp should be placed on each page to 
-    help with version control.
-\item[Internal Review:] After the draft version is finalized,
-    the next stage in the life-cycle might be to give the paper
-    to one or more colleagues for review. This stage is an internal review
-    process, as opposed to the formal review done upon submission
-    to the IEEE (see the next stage). Suggestions and 
-    criticism at this stage can very much improve the quality of the 
-    paper and can save much time in getting the paper 
-    published. The formatting for an internal review is fairly flexible. 
-    One requirement is that the paper contain a phrase to the effect that
-    the document is preliminary and should not be circulated without
-    permission of the author(s).  This can appear in the header or footer of
-    the paper, for example.
-\item[Submission for Review:] The next stage in the life-cycle is to 
-    submit the paper to the IEEE for formal review by anonymous reviewers. 
-    This review requires that the paper be formatted differently. In some 
-    cases, the title of the paper, and especially the authors' names, 
-    must be printed on a separate title page to ensure anonymity of the
-    authors. Double-spacing of the main text is usually required, but not 
-    time stamps, and so forth.
-\item[Initial Distribution:] While the document is submitted or 
-    ``in-press,'' it is desirable to be able to distribute the 
-    preliminary version (e.g., on the world-wide-web) for the 
-    benefit of other researchers. This, once again, will stipulate a 
-    different format. The paper should indicate that it is
-    ``submitted'' or ``in-press,'' and is not the final version, to 
-    avoid confusion between the preliminary and eventual printed
-    versions. The date is added on each page to further distinguish this
-    from the final version.
-\item[Final Form:] The IEEE uses its own software to format journal
-    papers. The ``final'' mode of the proposed macro package will
-    approximate the style of the published paper as closely as possible.
-    This allows the researcher to estimate page lengths, and to 
-    appropriately break equations and scale figures and tables. Perhaps 
-    if a standard set of macro packages is developed, the IEEE may 
-    eventually adopt it, and then the final-mode would be exactly 
-    what is published!
+Explicaremos el principio de funcionamiento de la herramienta distribuida 
+y sus principales objetivos, contrastando el flujo de trabajo con el de un 
+sistema de control de versiones centralizado. Básicamente que cada uno tiene 
+su propio repositorio, que las versiones pueden ser infinitas (por más que 
+haya una(s) maestra(s)), que se puede trabajar offline, etc.
 
-    For IEEE conferences, the author may (and often must) provide a
-    camera-ready formatted copy of the paper. In this case, the 
-    ``final'' mode of the macro package produces \emph{exactly} what 
-    is published.
-\item[Submission for Publishing:] After the paper is accepted,
-    and all the final corrections are made, it must be submitted for 
-    publishing. To submit a paper to an IEEE conference, the format of 
-    the paper is defined by the specifications used in the ``Final Form'' 
-    stage of the life-cycle. However, if the paper is to be submitted
-    to a journal, there are different formatting requirements for the
-    submitted document.
-\item[Final Distribution:] After the paper is published, it is
-    beneficial to have an electronic version of the paper
-    (e.g., for distribution on the world-wide-web). This final
-    version should have correct page numbers, the IEEE copyright 
-    information, the volume and issue number of the journal, and so forth.
-\end{description}
+\subsection{Atomic Commits}
 
-Clearly, it is cumbersome to \emph{manually} re-format a paper for all
-the stages of its life-cycle. We believe that a better solution is to
-use macro packages for individual text-processing systems which can
-automatically format a paper to certain specifications.  The format of
-the paper is automatically changed by changing a single parameter.
-This is not a dream! This has all been implemented for one
-text-processing system (see Section~\ref{sec:latex}), and our hope is
-that various readers and proponents of different text-formatting
-systems will volunteer to implement these specifications for their
-favorite text formatter. The entire research community will benefit
-from these efforts.
+En el sistema distribuido, hay una diferencia conceptual con los sistemas 
+centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
+más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
+entonces no hay preocupaciones como romper el build.
+
+\subsection{Branching and Merging}
+
+En un sistema distribuido, tener muchísimos branches es sencillo, de hecho 
+es más que sencillo, es "natural". Lo que permite un sistema distribuido es 
+no solo tener branches baratos sino también simplificar los merges.
+
+\subsection{Pushing and fetching/pulling}
+
+Estos dos conceptos son distintos al check in / check out centralizado, 
+consisten en el envío o recepción de commits entre dos repositorios. Aquí 
+explicaremos un poco en que consisten y cuando hay que usar uno u otro.
 
 %----------------------------------------------------------------------
-% SECTION III: Specifications
+% SECTION III: Should I use it in my project?
 %----------------------------------------------------------------------
-\section{Specifications}
+\section{Should I use it in my project?}
 
-In this section, we give specifications which we feel must be
-satisfied by a macro package to aid a researcher in preparing papers
-for publication. We have followed this list very closely when writing
-the example package \texttt{ieee.cls}.
+Explicar los casos donde resulta interesante aplicar esta herramienta. 
+También la idea es mostrar configuraciones posibles para la empresa donde 
+se vea la forma de hacer cosas que con un sistema no distribuido no sería 
+posible, o como es posible hacer lo mismo que se podía hacer con svn 
+(usando un repositorio que tenga el branch principal), de manera que 
+no te limita.
 
 %----------------------------------------------------------------------
-\subsection{Draft Manuscript}
+% SECTION IV: Then, why should I use it in my project?
+%----------------------------------------------------------------------
+\section{Then, why should I use it in my project?}
 
-The draft mode is the format used while the author writes the manuscript. 
-Its main characteristics are:
-\begin{itemize}
-\item Double spacing, single-column, and acceptably wide margins 
-      to allow room for comments and proofreaders' marks.
-\item A date-and-time stamp on each page to document the time of the
-      printing for help with version control.
-\item When figures belong to the manuscript, the author may switch
-      among the basic options:
-      \begin{enumerate}
-      \item Figures are not printed, but the appropriate space is
-            left in the manuscript.
-      \item Figures are not printed, and the captions are
-            included at the marked places with a small empty space.
-      \item Figures are inserted into the manuscript.
-      \item Figures are inserted one after the other at the end of the
-            manuscript. 
-      \item Figures are inserted, each on a separate page, at the end of the
-            manuscript. 
-      \end{enumerate}
-\end{itemize}
-
-%----------------------------------------------------------------------
-\subsection{Internal Review}
-The formatting requirements for an internal review are fairly loose.
-The following are suggestions:
-\begin{itemize}
-\item The following text should be included:
-      ``Preliminary version for evaluation: Please do not circulate 
-      without the permission of the author(s)''
-\item The figures should be included in the text, rather than at the
-      end of the document. 
-\item The text should be double-spaced, single-column, with wide enough 
-      margins to allow for reviewers' corrections.
-\item The date should be added to the header of each page. 
-\end{itemize}
-
-%----------------------------------------------------------------------
-\subsection{Submission for IEEE Formal Review}
-\label{sec:review}
-
-The following are desirable for submission to the IEEE:
-\begin{itemize}
-\item The printout would obligatorily be double-spaced, single-column.  
-\item The figures should be placed at the end of the paper and should
-      be identical to the figures to be submitted for publication if
-      the paper is accepted.
-\item As some of the Transactions require a separation of the title
-      page and the text to provide anonymity, this should be an
-      option. 
-\item The date of submission should be added on the title page 
-      and the second page if a separate title page is generated.
-\end{itemize}
-
-%----------------------------------------------------------------------
-\subsection{Transactions-like Printing for Evaluation and Length
-Measurement}
-
-This format should follow as precisely as practicable the format of the 
-journal.
-
-%----------------------------------------------------------------------
-\subsection{Submission for Publication in a Journal}
-
-This could be nearly identical to the case in
-Section~\ref{sec:review}.  A mark should be placed in the text to show
-about where each figure should go.  Figures may optionally be printed
-at a larger scale to allow better photographic reproduction.  The date
-of submission and possibly the editor's paper number should be added.
-
-%----------------------------------------------------------------------
-\subsection{Camera-ready Form for Conference Submission}
-
-This is the only format that has a very strict and exactly defined
-layout.  This layout will be defined separately for each conference,
-on the basis of the its author's guide.
-
-%----------------------------------------------------------------------
-\subsection{Electronic Distribution (Initial and Final)}
-
-A hardcopy or electronic version of the paper can be useful for
-distribution during various stages in its life-cycle, but improper
-information in this distributed form can lead to misunderstanding.
-The format should provide some specific information.
-\begin{itemize}
-\item If the paper is currently submitted for review, the
-      text ``Submitted to (journal or conference name) for
-      publication,'' along with the date, should appear on the title
-      page.  
-\item If the paper has been accepted for publication, but is not
-      yet printed, the text ``Accepted for publication by (journal or
-      conference name), (in-press)'' should appear. 
-\item In addition, for both of the above situations, the following text 
-      should be included: ``Preliminary version: Please do not circulate 
-      without the permission of the author(s).''
-\item If the version is a reprint, the 
-      text ``Reprinted from (journal or conference name)'' should be 
-      included. Additionally, the page numbers should match the printed
-      version, and the volume number, issue number and IEEE copyright 
-      information should be included. 
-\item To facilitate the paper's distribution on the world-wide-web,
-      the height should be set 
-      in a way that it can be printed both on A4 and U.S. letter-size paper. 
-      A ``full'' A4 page cannot usually be printed in the United 
-      States; the top lines will be missing. 
-\end{itemize}
-This form should allow a lot of freedom, such as one- or two-column
-formatting, the inclusion of a cover page, and so on.
-
-%----------------------------------------------------------------------
-% SECTION IV: The LaTeX2e Class
-%----------------------------------------------------------------------
-\section{The \latexiie\ Class}
-\label{sec:latex}
-
-One text-formatting package in common use by researchers is the
-\latexiie\ system~\cite{lamport}. Some of its features include a very
-flexible macro capability, excellent formatting of mathematical
-equations, seamless integration of text into graphics (using the
-\texttt{psfrag.sty} package; see~\cite{goossens}), and affordable
-price (it's free!).
-
-Documents formatted with \latexiie\ must belong to a certain ``class.''
-A class file is a set of macros which tells \latexiie\ how to format
-the document. For example, the standard classes which are available
-include an article class, a report class, a book class and a letter
-class.
-
-For the purpose of writing IEEE papers, we have developed a special
-\latexiie\ ``class'' file. Users of \LaTeX\ probably know about
-\texttt{IEEEtran.sty}, written by Murray and Balemi. This style was 
-originally devised for evaluation and length measurement, but it is
-close to meeting some of the above desires. It was written for the
-now-obsolete \LaTeX 2.09, and has been modified for \latexiie\ by
-N\"{u}chter. The latter, called \texttt{IEEEtran.cls}, may be found on
-the IEEE world-wide-web site.  It implements much of the functionality
-required for the ``Final Form'' stage of the document life-cycle. We
-found it helpful as a starting point for this project. Our modified
-version, called \texttt{ieee.cls}, satisfies all of the requirements
-for each stage of the document life-cycle.
-
-\subsection{Choosing the Paper's Style}
-
-Documents written for \latexiie\ are written as plain text. The
-\latexiie\ system converts the text into formatted pages. To tell
-\latexiie\ how to format your document, certain commands need to be
-entered into the text.
-
-The \texttt{ieee.cls} class file makes this very easy.  The first line
-of your document needs to specify a command of the form
-\begin{verbatim}
-  \documentclass[main-mode,
-                 sub-mode,
-                 misc-options]{ieee}
-\end{verbatim}
-where one ``main-mode'' is chosen from the following:
-\begin{description}
-\item[\texttt{draft}] Double-spaced, single-column, with date and time
-     stamp.
-\item[\texttt{submission}] Double-spaced, suitable for submitting the
-     paper for review, or for submitting the paper for publishing.
-\item[\texttt{compressed}] Same as ``submission,'' only single-spaced.
-     This is suitable for archival, internal review, and for some 
-     conference proceedings. 
-\item[\texttt{final}] For IEEE journals, this mode approximates the
-     journal's final form. For IEEE conferences, it formats
-     the paper for a camera-ready printout.
-\end{description}
-The optional ``sub-mode'' is chosen from the following:
-\begin{description}
-\item[\texttt{internal}] The internal sub-mode can modify either the
-    ``submission,'' 
-    ``compressed,'' or ``final'' modes. It changes the header to notify 
-    the reader that this is an evaluation preprint, and not to be
-    distributed. 
-\item[\texttt{submitted}] The submitted sub-mode can modify either the
-    ``compressed'' or ``final'' modes. It changes the header to notify 
-    the reader that this paper has been submitted to a certain journal 
-    for publication, and that it is not to be distributed.
-\item[\texttt{inpress}] The inpress sub-mode is similar to the submitted 
-    sub-mode. It can modify either the ``compressed'' or ``final'' modes. 
-    It changes the header to notify the 
-    reader that this paper has been accepted by a certain journal for 
-    publication, but that it has not yet been published. It specifies that 
-    the paper is not to be distributed.
-\item[\texttt{reprint}] The reprint sub-mode can modify only the ``final''
-    mode. It changes the header to state that the paper is reprinted
-    from a certain journal. It includes proper page numbers, IEEE
-    copyright information and the IEEE log number.
-\item[\texttt{technote}] When used in combination with ``final,''
-    this sub-mode produces a two-column technical note.
-\end{description}
-The optional ``misc-options'' are chosen from the following:
-\begin{description}
-\item[\texttt{titlepage/notitlepage}] The titlepage option causes a
-    separate title page to be produced. The notitlepage option 
-    (default) does not produce a separate title page.
-\item[\texttt{anonymous}] By default, all author information is included
-    in the typeset paper.
-    However, if the ``anonymous'' option is selected, author information
-    is omitted from the paper (except for on the optional title page).
-    Author information is omitted from the title line on the first
-    page of the paper and from the header on all pages. The author's
-    affiliation is omitted from the first page, and the author's 
-    biography is also omitted. Anonymity may be required when
-    submitting a paper for review.
-\item[\texttt{invited}] If the paper is an invited paper (as this
-    one is), the ``invited'' option prints \emph{(Invited Paper)} under the 
-    authors' names on the first page of the paper.
-\item[\texttt{9pt,10pt,11pt,12pt}] You may manually choose the paper's 
-    type size.
-    You should not need to do this since the ``correct'' size is
-    automatically chosen. However, if you want, you may use these to
-    change the type size of the main text. (``9pt'' is a bit of a hack
-    to retain backward-compatibility.)
-\item[\texttt{narroweqnarray}] This fixes a \LaTeX\ bug. The
-    spacing around the ``='' sign in equation arrays is changed 
-    to be the same as in displayed math.  
-\item[\texttt{inline}] Compresses the horizontal spacing of in-text
-    math equations. The authors think that the resulting equations
-    look better than those normally produced by \latexiie.
-\end{description}
-
-Already we can see the power of \texttt{ieee.cls}. By changing a
-single parameter in the first line of the document, the user can
-change the entire format of the paper!
-
-\subsection{Plug-Ins}
-
-The main \texttt{ieee.cls} file specifies the formatting required for
-a generic IEEE journal. However, some journals have their own
-formatting particularities. For example, journals of the IEEE Signal
-Processing Society have centered figure captions, and all other
-journals have left-justified captions. Journals of the IEEE Computer
-Society are formatted very differently from journals of all other
-societies. Furthermore, each conference has its own style.
-
-Rather than burdening the main \texttt{ieee.cls} file with the
-definitions required for each journal, we have placed this task on
-small ``plug-in'' files designed to work with \texttt{ieee.cls}. For
-example, to format a document for the IEEE Transactions on Computers,
-specify (after the \verb|\documentclass| command):
-\begin{verbatim}
-  \usepackage{ieeetc}
-\end{verbatim}
-Plug-in files are also used to format papers for conferences. The 
-main mode of the paper should be ``final,'' and the 
-conference style-file should be loaded. For example,
-\begin{verbatim}
-  \usepackage{ieeeimtc}
-\end{verbatim}
-specifies the style needed for the IEEE Instrumentation and
-Measurement Technology Conference.
-
-At the moment, plug-in files exist for almost all of the IEEE journals
-(see the world-wide-web site mentioned in the Conclusion for
-up-to-date information on which are supported), but only a few
-conferences.  However, as the use of the \texttt{ieee.cls} package
-increases, additional plug-ins will be created.
-
-\subsection{More Definitions}
-
-In addition to specification of the modes and options for the paper,
-several more things need to be defined. For a regular IEEE journal
-submission, define the journal name in the form
-\begin{verbatim}
-  \journal{IEEE Trans.\ Something}
-\end{verbatim}
-The journal name is used to compose the header for each page.  To add
-any other information after the journal name, use \verb|\titletext|.
-For example, to indicate the editor's manuscript number on a preprint,
-you would type something like
-\begin{verbatim}
-  \titletext{, TN\#9999.}
-\end{verbatim}
-
-The date is printed in the header for certain combinations of document
-options (e.g., for the submission mode). If you would like to pre-date
-or post-date the article, type, for example,
-\begin{verbatim}
-  \renewcommand{\today}{July 4, 1776}
-\end{verbatim}
-To specify the IEEE copyright information on the first page of a
-reprint, type
-\begin{verbatim}
-  \ieeecopyright{xxx--xxxx/97\$10.00 
-    \copyright\ 1997 IEEE}
-\end{verbatim}
-
-Reprints also contain either an ``IEEE log number,'' a ``publisher
-item identifier,'' or similar publishing information in the lower left
-column on the first page. This can be entered as
-\begin{verbatim}
-  \lognumber{xxxxxxx}
-\end{verbatim}
-or
-\begin{verbatim}
-  \pubitemident{S xxxx--xxxx(97)xxxxx--x}
-\end{verbatim}
-or
-\begin{verbatim}
-  \loginfo{Manuscript received... }
-\end{verbatim}
-To specify the first page of a reprint of a paper beginning on page 
-103 of a journal, you would type
-\begin{verbatim}
-  \firstpage{103}
-\end{verbatim}
-Finally, for a conference, the location and date are specified as, for
-example,
-\begin{verbatim}
-  \confplacedate{Ottawa, Canada,  
-                 May 19--21, 1997}
-\end{verbatim}
-
-\subsection{The Title Information}
-
-The title-and-author information for a paper is entered as follows.
-Define:
-\begin{verbatim}
-  \title[Short Title]{Title of paper}
-  \author[Short Names]{First 
-     Author\member{Student 
-     Member}\authorinfo{Department 
-     of Electrical Engineering\\ 
-     Some University, Somewhere CA, 
-     90210, USA}% 
-  \and{}Second Author\member{Senior 
-     Member}\authorinfo{Department 
-     of Electrical Eng...}
-  \and{}and Third 
-     Author\member{Fellow}\authorinfo{...}
-  }
-\end{verbatim}
-
-The \verb|\title| command may be used with or without the optional
-first parameter specified within square brackets. If the parameter is
-present, it is used as the title placed in the header on each page.
-Otherwise, the actual title is used for both the header and the title
-page.
-
-Entering the author information is perhaps the most complicated part
-of using this class. However, if the above template is used,
-everything should work well. \emph{Note that some types of documents
-ignore some of the author information.} For example, conference
-proceedings and technical notes do not print IEEE membership
-information.
-
-As with the title command, there is an optional first parameter. If it
-is specified, it is used as the authors' names for the header on every
-odd page of an final-mode manuscript, for example.  Otherwise, no
-author information is printed in the header.
-
-The membership status of an author is entered via the 
-\verb|\member| command, and the author's affiliation is specified
-with the \verb|\authorinfo| command.  Note that the content required
-in the \verb|\authorinfo| command tends to vary depending on whether
-the paper is for a conference or for a journal. The number of manual
-changes are small, and must be done by a human anyway. The example
-given is for an IMTC conference.
-
-Finally, note that the authors are separated by an \verb|\and|
-command.  This command \emph{does not} insert the word ``and'' between
-author names, but allows \latexiie\ to separate them intelligently. If
-the word ``and'' is required before the final author's name, it must
-be inserted additionally.
-
-The title page or lines are actually produced by the command
-\begin{verbatim}
-  \maketitle
-\end{verbatim}
-
-\subsection{Document Preliminaries}
-
-Users of the old \texttt{IEEEtran.sty} style will find the rest of the
-instructions to be very familiar. The abstract is specified
-\begin{verbatim}
-  \begin{abstract} 
-  ...
-  \end{abstract}
-\end{verbatim}
-The keywords (or index terms) are specified via
-\begin{verbatim}
-  \begin{keywords}
-  ...
-  \end{keywords}
-\end{verbatim}
-
-\PARstart Many of the IEEE journals typeset the first character to be
-two lines tall, as in this paragraph. Furthermore, the rest of the
-first word is set in capital letters. This can be done using the
-command
-
-\unskip
-\begin{verbatim}
-  \PARstart Many of the IEEE...
-\end{verbatim}
-
-\PARstartCal Just for fun, and perhaps to make your draft submissions
-look a little snazzy, you can also start the first paragraph with a
-calligraphic character by, for example,
-
-\unskip
-\begin{verbatim}
-  \PARstartCal Just for fun...
-\end{verbatim}
-
-The user should be aware that these larger characters may not be
-available on all systems, and \latexiie\ may need to run
-{\font\mf=logo10 \mf METAFONT} to generate them.
-
-The main body of the paper is written according to standard \latexiie\
-convention. We should also mention that, as with the package
-\texttt{IEEEtran.cls}, theorems and proofs may be defined as in this
-example: 
-\begin{verbatim}
-  \newtheorem{theorem}{Theorem}
-  ...
-  \begin{theorem}[Theorem name]
-    Consider the system ...
-  \end{theorem}
-  \begin{proof}
-    The proof is trivial.
-  \end{proof}
-\end{verbatim}
-
-\subsection{The End of the Paper}
-
-The references in the paper are formatted with {\sc Bib}\TeX\ via the
-special IEEE {\sc Bib}\TeX\ style file \texttt{IEEEbib.bst}. This file
-has not been modified by us, and may be found on the IEEE
-world-wide-web server.  To use it, insert the following lines in your
-paper where the references are to be placed:
-\begin{verbatim}
-  \bibliographystyle{IEEEbib}
-  \bibliography{filename}
-\end{verbatim}
-where \texttt{\emph{filename.bib\/}} is the name of the
-bibliography data\-base file comprising all your {\sc Bib}\TeX\ entries.
-The \latexiie\ manual explains how to use {\sc Bib}\TeX\ and how to
-create bibliography files.
-
-Finally, regular journal papers should include the biographies of
-their authors.  This may be done simply as shown in the following:
-\begin{verbatim}
-  \begin{biography}{Istv\'{a}n Koll\'{a}r} 
-  (M'87--SM'93--F'97) was born...
-
-  From September 1993 to June 1995, ... 
-  \end{biography}
-\end{verbatim}
-An optional first parameter specifies the file that contains the 
-author's ``photograph.''
-\begin{verbatim}
-  \begin{biography}[face.ps]{Gregory L. 
-  Plett} (S'97) was born ...
-  \end{biography}
-\end{verbatim}
-This can be especially useful for preprints and reprints of the
-document.  If you do not specify this first parameter, a framed empty
-box is printed; however, any file that is recognized by
-\verb|\includegraphics| may be used.  The aspect ratio of the
-photograph should be approximately 25 by 32.  If it is a few percent
-away from the desired aspect ratio, the picture is re-sized
-non-proportionally.  Otherwise, it is shrunk proportionally to fit the
-space and is then placed, centered, in a box of the correct size; a
-warning message ``Too wide/tall'' is printed.
-
-Note that a single blank line in the biography environment causes
-paragraph separation. But beware: Multiple blank lines in a row will
-leave a larger vertical space between paragraphs.
-
-%----------------------------------------------------------------------
-% SECTION V: Putting it all Together
-%----------------------------------------------------------------------
-\section{Putting it all Together}
-
-To be perfectly clear, Fig.~\ref{fig-example} summarizes the commands
-necessary to format a document using the \texttt{ieee.cls} file. The
-\latexiie\ source for this paper is also available at the
-world-wide-web site mentioned in the Conclusion, furnishing a more
-complete example.
-
-\begin{figure}[htb]
-\begin{center}\small
-\begin{tabular}{|l|}\hline
-\begin{minipage}{0.9\hsize}
-\vspace{3mm}
-{\small
-\begin{verbatim}
-\documentclass[final]{ieee}
-
-\begin{document}
-
-\title[Specification for ...]{%
-   Specification for ...}
-
-\author[PLETT AND KOLL\'{A}R]{%
-   Gregory L. Plett\member{Student 
-   Member},\authorinfo{G.\ L.\ 
-   Plett is ...}
-\and{}and Istv\'{a}n 
-   Koll\'{a}r\member{Fellow}\authorinfo{I.\
-   Koll\'{a}r is ...}
-}
-
-\journal{IEEE Transactions on ...}
-
-\maketitle
-
-\begin{abstract}
-Our premise...
-\end{abstract}
-
-\begin{keywords}
-Style file...
-\end{keywords}
-
-\section{Introduction}
-\PARstart An important aspect of...
-
-\bibliographystyle{IEEEbib}
-\bibliography{bib-file}
-
-\begin{biography}{Gregory L. Plett} (S'97)
-...
-\end{biography}
-
-\end{document}
-\end{verbatim}
-}
-\vspace{1mm}
-\end{minipage} \\ \hline
-\end{tabular}
-\end{center}
-\caption{Input used to produce this paper.}
-\label{fig-example}
-\end{figure}
-
-\section{Figures}
-
-Figures in the text require special attention. First, when submitting
-a paper for printing, it is often required that the figures and tables
-be at the end of the paper. This can be handled by the
-\texttt{endfloat.sty} package, which is part of the standard \latexiie\
-distribution.
-
-The documentation for the ``endfloat'' package is somewhat daunting,
-but all that should be required is to specify
-\begin{verbatim}
-  \usepackage{endfloat}
-\end{verbatim}
-before the \verb+\begin{document}+ command in the paper. The default 
-options should work well.
-
-Whether or not you use the \texttt{endfloat.sty} package, encapsulated
-postscript (EPS) files may be included simply in the text by
-\begin{verbatim}
-  \includegraphics{figname.eps}
-\end{verbatim}
-Partial documentation for the \verb|\includegraphics| command is
-available in the \latexiie\ user's guide~\cite{lamport,goossens}, and
-complete documentation is available in \texttt{epslatex.ps}, included
-in the standard distribution of \latexiie. The reader should note that
-the new \verb|\includegraphics| command supersedes the older
-style-packages \texttt{epsfig.sty} and \texttt{psfig.sty}, which are
-no longer required.
-
-The reader may also wish to investigate the very powerful
-\texttt{psfrag.sty} package, which is again part of the
-standard distribution. It allows one to change labels in EPS files to
-use \LaTeX's fonts, and it produces a very polished looking paper.
-
-\subsection{Figure Management with \protect{\tt\lowercase{ieeefig.sty}}}
-
-Finally, we have developed another package to aid in figure
-preparation. It is called \texttt{ieeefig.sty}, and is especially
-suited for use with the \texttt{psfrag.sty} package.  It provides a
-practical method to manage a large number of figures efficiently.  It
-is designed to work with \texttt{ieee.cls}, but will also work with
-all of the standard \latexiie\ classes (e.g., for writing reports,
-writing books, or creating presentation transparencies).  The
-\texttt{ieeefig.sty} package is loaded by specifying (after the
-\verb|\documentclass| command)
-\begin{verbatim}
-  \usepackage[options]{ieeefig}
-\end{verbatim}
-The options will be discussed shortly.
-
-To use the \texttt{ieeefig.sty} package, you must place each figure in
-its own \latexiie\ file (e.g., \texttt{\emph{figname.tex}}). The file
-\texttt{\emph{figname.tex}} contains all of the commands necessary to
-produce the figure. These commands might include \verb|\psfrag|
-commands to replace labels in an EPS file with \LaTeX\ formatted text,
-and the command necessary to load the EPS file.
-
-The figure is included in the text of the paper via the following
-commands:
-\begin{verbatim}
-  \begin{figure}
-    \figdef[dim]{figname}
-    \caption{This figure...}
-    \label{fig:figname}
-  \end{figure}
-\end{verbatim}
-It is automatically centered in its column. (The optional argument in
-square brackets, ``dim,'' is the vertical size of the figure. It
-defines the amount of vertical space to be skipped if the ``blank''
-option is used.)
-
-Through separation of the figure-generating commands from the main
-paper, the figure is portable and may be re-used in other papers,
-reports or presentations. It also permits \texttt{ieeefig.sty} to
-perform some useful tasks. These tasks are controlled either by the
-options used when loading the style or by a series of commands. The
-available options may be chosen from the following:
-\begin{description}
-\item[\texttt{draft}] Displays the filename \texttt{\emph{figname.tex\/}} in the
-    margin. Also displays the height of the figure. In this way, you can
-    determine the correct value of the optional argument ``dim'' of the 
-    \verb|\figdef| command.
-\item[\texttt{final}] Does not display the filename or height of the figure.
-\item[\texttt{blank}] Instead of displaying figures, 
-    \verb|\figdef| will leave a vertical space on the page.  The height of 
-    the vertical space is specified by the optional argument ``dim'' of the 
-    \verb|\figdef| command. By omitting figures, you will
-    allow 
-    \latexiie\ to compile your document more quickly. This option may also 
-    be selected in the document by the command \verb|\draftfigstrue|.
-\item[\texttt{noblank}] This is the complement of the 
-    \texttt{blank} option. Figures are shown. This option may also be
-    selected in the document via the command \verb|\draftfigsfalse|.
-\item[\texttt{frame}] This option causes each figure to be surrounded
-    by a box, which can help determine whether the bounding box 
-    on an EPS file is correct. The bounding box often must be adjusted if the
-    \texttt{psfrag.sty} package is being used and labels go outside the 
-    boundary of the figure. If the bounding box is incorrect, the figure
-    will not be centered properly, and the spacing before and after the 
-    figure will be incorrect. To adjust the bounding box, see the
-    \texttt{trim} command below. This option may also be selected in the
-    document using the command \verb|\figframestrue|.
-\item[\texttt{noframe}] Frames are not drawn around figures. This option
-    may also be selected in the document through the command
-    \verb|\framefigsfalse|.
-\end{description}
-
-If EPS files are being loaded in the \texttt{\emph{figname.tex\/}} file, they
-should be loaded using the command
-\begin{verbatim}
-  \inserteps[trim=a b c d]{figname.eps}
-\end{verbatim}
-This command inserts the EPS file \texttt{\emph{figname.eps}} at the correct
-scale. It also adjusts the bounding box by trimming off \texttt{\emph{a}}, 
-\texttt{\emph{b}}, \texttt{\emph{c}}, and \texttt{\emph{d}} points from 
-the left, bottom, right and top
-edges of the figure, respectively. Negative trim amounts increase the
-size of the bounding box. If any \verb|\psfrag| statements have been
-made for this figure, they will take effect with this command.
-
-Finally, to scale all EPS figures by a constant ``num'' use
-\begin{verbatim}
-  \setfigscale{num}
-\end{verbatim}
-This is very useful for specifying different scales for presentation
-transparencies and for reports. If the \verb|\setfigscale| command is
-in the main paper text, then it applies to all figures from that point
-in the paper onward. If it is inside of an individual
-\texttt{\textit{figname.tex\/}} file, then it applies only to that
-figure.
-
-%----------------------------------------------------------------------
-% SECTION VI: Wish List
-%----------------------------------------------------------------------
-\section{Wish List for \protect{\tt\lowercase{ieee.cls}}}
-
-The \latexiie\ class package, \texttt{ieee.cls}, used in conjunction
-with the \texttt{endfloat.sty} and \texttt{ieeefig.sty} packages
-provides nearly all the desired functionality of a package to format
-IEEE papers.  Several things remain outstanding, however.
-
-The biggest omission is that ``plug-ins'' exist for only a few
-conferences.  We hope that researchers who have developed styles for
-other IEEE conferences will modify their styles to fit within the
-\texttt{ieee.cls} framework, and will then contribute their work to
-the scientific community.
-
-A more subtle issue is that none of the two-column modes balance the
-columns on the last page of the paper. The standard package
-\texttt{multicol.sty} may be able to help, but it apparently does not
-allow single-column figures and tables. Perhaps some {\TeX}pert out
-there can fix this. Right now, the only work-around is for the user to
-manually insert a \verb|\newpage| at the appropriate place to try to
-balance the columns on the last page of the paper. This is a poor
-solution at best.
-
-Finally, the multi-blank-line bug in the biography environment should
-be fixed. Until it is, the work-around is to be careful to leave only
-a single blank line between paragraphs.
+Explicar los casos donde resulta interesante aplicar esta herramienta. 
+También la idea es mostrar configuraciones posibles para la empresa donde 
+se vea la forma de hacer cosas que con un sistema no distribuido no sería 
+posible, o como es posible hacer lo mismo que se podía hacer con svn 
+(usando un repositorio que tenga el branch principal), de manera que 
+no te limita.
 
@@
 
-We have outlined a specification for macro packages to aid an author
-of papers for IEEE publications. Additionally, we have provided a
-\latexiie\ class which accomplishes most of these goals. Users of other
-text-formatting systems are encouraged to write similar macro packages
-for the benefit of the research community. Anyone interested in this 
-task should contact the second author via e-mail.
-
-The \latexiie\ class, which was used as an example here,
-is provided on an ``as-is'' basis at
-
-\begin{verbatim}
-  http://www-isl.stanford.edu/ieee/
-\end{verbatim}
-
-\noindent or at
-
-\begin{verbatim}
-  ftp://isl.stanford.edu/pub/ieee/
-\end{verbatim}
-
-\noindent Any bug report is welcome, especially if accompanied by the solution!
-Reports should be made, via e-mail, to the first author.
-
-A similar macro package is under development for users of Microsoft Word. 
-It is available at
-
-\begin{verbatim}
-  http://www.ifm.liu.se/Meastech/Bjorn/IMTC.html
-\end{verbatim}
-
-\noindent At the present time, it is able to format papers for the IEEE
-Instrumentation and Measurement Technology Conference. 
-References to both packages can also be found on the IM Society page
-
-\begin{verbatim}
-  http://www.ieee.org/society/im/im.htm
-\end{verbatim}
-
-We hope that this paper sparks interest and imagination. We also hope
-that the \latexiie\ and Microsoft Word classes save many researchers much work.
+\emph{to be done}
 
 %----------------------------------------------------------------------
-% The bibliography. This bibliography was generated using the following
-% two lines:
-%\bibliographystyle{IEEEbib}
-%\bibliography{ieeecls}
-% where, the contents of the ieeecls.bib file was:
-%
-%@book{lamport,
-%        AUTHOR = "Leslie Lamport",
-%         TITLE = "A Document Preparation System: {\LaTeX} User's Guide
-%                  and Reference Manual",
-%       EDITION = "Second",
-%     PUBLISHER = "Addison-Wesley",
-%       ADDRESS = "Reading, MA",
-%          YEAR = 1994,
-%          NOTE = "Be sure to get the updated version for \LaTeX2e!"
-%}
-%
-%@book{goossens,
-%        AUTHOR = "Michel Goossens and Frank Mittelbach and
-%                  Alexander Samarin",
-%         TITLE = "The {\LaTeX} Companion",
-%     PUBLISHER = "Addison-Wesley",
-%       ADDRESS = "Reading, MA",
-%          YEAR = 1994,
-%}
-%
-% The ieeecls.bbl file was manually included here to make the distribution
-% of this paper easier. You need not do it for your own papers.
 
@@
 
-\bibitem{lamport}
-Leslie Lamport,
-\newblock {\em A Document Preparation System: {\LaTeX} User's Guide and
-  Reference Manual},
-\newblock Addison-Wesley, Reading, MA, 2nd edition, 1994.
-\newblock Be sure to get the updated version for \latexiie!
+% \bibitem{lamport}
+% Leslie Lamport,
+% \newblock {\em A Document Preparation System: {\LaTeX} User's Guide and
+%   Reference Manual},
+% \newblock Addison-Wesley, Reading, MA, 2nd edition, 1994.
+% \newblock Be sure to get the updated version for \latexiie!
+% 
+% \bibitem{goossens}
+% Michel Goossens, Frank Mittelbach, and Alexander Samarin,
+% \newblock {\em The {\LaTeX} Companion},
+% \newblock Addison-Wesley, Reading, MA, 1994.
 
-\bibitem{goossens}
-Michel Goossens, Frank Mittelbach, and Alexander Samarin,
-\newblock {\em The {\LaTeX} Companion},
-\newblock Addison-Wesley, Reading, MA, 1994.
+\bibitem{linusgit}
+Linus Torvalds
+\newblock Google Talk presentation on Git
 
@@
 
-\begin{biography}{Gregory L. Plett} 
-(S'97) was born in Ottawa, ON, in 1968. He received the B.Eng.\ degree
-in computer systems engineering with high distinction from Carleton
-University, Ottawa, in 1990, and the M.S.\ degree in electrical
-engineering from Stanford University, CA, in 1992.  He is currently a
-Ph.D.\ candidate at Stanford University, where he is researching
-aspects of adaptive control under the supervision of Professor Bernard
-Widrow.
-\end{biography}
-
-\begin{biography}{Istv\'{a}n Koll\'{a}r} 
-(M'87--SM'93--F'97) was born in Budapest, Hungary, in 1954. He graduated 
-in electrical engineering from the Technical University of Budapest in 
-1977 and in 1985 received the degree ``Candidate of Sciences'' (the 
-equivalent of Ph.D.) from the Hungarian Academy of Sciences, and the 
-degree dr.tech.\ from the Technical University of Budapest.
-
-From September 1993 to June 1995, he was a Fulbright Scholar and
-visiting associate professor in the Department of Electrical
-Engineering, Stanford University. He is professor of electrical
-engineering, Department of Measurement and Information Systems,
-Technical University of Budapest. His research interests span the
-areas of digital and analog signal processing, measurement theory, and
-system identification. He has published about 50 scientific papers and
-is coauthor of the book \emph{Technology of Electrical Measurements},
-(L.\ Schnell, ed., Wiley, 1993). He authored the \emph{Frequency
-Domain System Identification Toolbox} for Matlab.
-\end{biography}
-
 \end{document}

### 2010-04-25 paper.tex
escribi un poquito de la intro

@@
 
-\confplacedate{Buenos Aires, Argentina, April 18, 2010}
+%\confplacedate{Buenos Aires, Argentina, April 18, 2010}
 
@@
 
-\PARstart Vamos a contar cuando surgió esta tecnología y sus principales 
+\PARstart
+
+%It is given that, in these times, modern software projects need a tool to 
+%automatically track changes made in the source files, called Version Control Systems (VCS).
+
+Version Control Systems (VCS) usually track the whole history of the
+source code in a central server that everyone that can access. This 
+central server contains all the changes and branches of the code and 
+the users that can read the versions or commit changes have to connect 
+to this repository.
+Distributed Version Control Systems (DVCS) are a modern way of managing
+revisions of software that do not have a centralized server, for this reason 
+they are also called De-centralized Version Control Systems. Everybody has a 
+copy of the full repository with all changes made in the history.
+
+Vamos a contar cuando surgió esta tecnología y sus principales 
 exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 

### 2010-04-25 paper.tex
expansion de la introduccion

@@
 
-\PARstart
-
 %It is given that, in these times, modern software projects need a tool to 
@@
 
-Version Control Systems (VCS) usually track the whole history of the
+\PARstart Version Control Systems (VCS) usually track the whole history of the
 source code in a central server that everyone that can access. This 
@@
 the users that can read the versions or commit changes have to connect 
-to this repository.
+to this repository. The most popular today example of this approach is SVN, which is a 
+widely used VCS.
+
 Distributed Version Control Systems (DVCS) are a modern way of managing
@@
 
-Vamos a contar cuando surgió esta tecnología y sus principales 
-exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
-similitudes con otros sistemas de versionado distribuidos como Mercurial. 
-Un poco se contará las diferencias fundamentales entre las herramientas de 
-versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
-pero no explicándolas.
+The concept of distributed repositories came up first on the commercial product 
+Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
+on to design BitKeeper, another commercial VCS which expanded on those ideas. 
+BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
+the license to use BitKeeper was finished. 
+To replace the use of BitKeeper in the Linux kernel, two projects started, Git and 
+Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
+developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
+the idea of tracking only patches and not versions.
 
-La idea del paper sería contar las ventajas que puede 
-tener este esquema dentro de un ambiente enterprise de código cerrado, en contraste 
-a un ambiente open source donde el esquema distribuido tiene incluso más sentido.
+%Vamos a contar cuando surgió esta tecnología y sus principales 
+%exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
+%similitudes con otros sistemas de versionado distribuidos como Mercurial. 
+%Un poco se contará las diferencias fundamentales entre las herramientas de 
+%versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
+%pero no explicándolas.
+
+We're going to do a comparison between centralized and decentralized control version systems,
+highlighting the differences and advantages and disadvantages of both approachs in various 
+contexts, both on a conceptual and practical level. In this paper we'll base our explanations 
+on Git but there are no big differences between 
+most of these DVCS, especially between Git and Mercurial that are largely similar, with 
+most commands having the same names in both tools.
+
+%La idea del paper sería contar las ventajas que puede 
+%tener este esquema dentro de un ambiente enterprise de código cerrado, en contraste 
+%a un ambiente open source donde el esquema distribuido tiene incluso más sentido.
 

### 2010-04-25 paper.tex
agregado algo de architecture

@@
 
-Explicaremos el principio de funcionamiento de la herramienta distribuida 
-y sus principales objetivos, contrastando el flujo de trabajo con el de un 
-sistema de control de versiones centralizado. Básicamente que cada uno tiene 
-su propio repositorio, que las versiones pueden ser infinitas (por más que 
-haya una(s) maestra(s)), que se puede trabajar offline, etc.
+In a DVCS like Git, everybody has the full repository in their hard drives.
+Since there is no central server, operations on the repository all are done 
+offline. This means that actions like commiting do not depend on having a 
+network connection, since commits are made on your repository.
+
+Changes can thus be shared between everyone passing changes between repositories, 
+without the need of making those changes in a central repository.
+
+% Explicaremos el principio de funcionamiento de la herramienta distribuida 
+% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
+% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
+% su propio repositorio, que las versiones pueden ser infinitas (por más que 
+% haya una(s) maestra(s)), que se puede trabajar offline, etc.
+
+% -habria que agregar una imagen de muetsra
 
@@
 
-En el sistema distribuido, hay una diferencia conceptual con los sistemas 
-centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
-más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
-entonces no hay preocupaciones como romper el build.
+In a centralized VCS, most of the time commits aren't done until you are sure that 
+the change is well written and can be actually shared to everybody else, since the 
+commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
+change, since commits are made in the local repository, they tend to be more atomic, 
+and commits aren't huge changesets but can be logical, coherent changes.
+To do this in a centralized VCS, one would have to create a new branch of the source code, 
+and then merge the branch, but creating and merging branches all the time is 
+resource-consuming, and branches are seen by everybody in the 
+%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
+%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
+%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
+%entonces no hay preocupaciones como romper el build.
 

### 2010-04-25 paper.tex
termine la oracion

@@
 and then merge the branch, but creating and merging branches all the time is 
-resource-consuming, and branches are seen by everybody in the 
+not effortless, and branches are seen by everybody that can access the repository, 
+so this is not always done.
 %En el sistema distribuido, hay una diferencia conceptual con los sistemas 

### 2010-04-25 paper.tex
add fetch/pull

@@
 
-Estos dos conceptos son distintos al check in / check out centralizado, 
-consisten en el envío o recepción de commits entre dos repositorios. Aquí 
-explicaremos un poco en que consisten y cuando hay que usar uno u otro.
+When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
+Push refers to taking all my changes and add them to the repository of another co-worker
+Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
+At the same way, another co-worker can do Pull over my repo and get my new code & changes
+
+%Estos dos conceptos son distintos al check in / check out centralizado, 
+%consisten en el envío o recepción de commits entre dos repositorios. Aquí 
+%explicaremos un poco en que consisten y cuando hay que usar uno u otro.
 

### 2010-04-25 paper.tex
expansion en la seccion de architecture

--- 2010-04-25 paper.tex
@@
 
+Operations being done offline also means that there is no network latency to be worried of,
+and can be more performant. Performance is important in VCS because if the revision
+system is too slow, it might affect the workflow of the tool. Operations like commits, 
+searching through the history, taking the diff out of two branches,  
 % Explicaremos el principio de funcionamiento de la herramienta distribuida 
@@
 In a centralized VCS, most of the time commits aren't done until you are sure that 
-the change is well written and can be actually shared to everybody else, since the 
-commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
-change, since commits are made in the local repository, they tend to be more atomic, 
+the change is well tested and can be actually shared to everybody else, since the 
+commit is going to be shared as soon as it's done, and could ``break the build''. 
+In a DVCS the nature of the commits change, since commits are made in the local 
+repository, they tend to be more atomic, 
 and commits aren't huge changesets but can be logical, coherent changes.
@@
 so this is not always done.
+
 %En el sistema distribuido, hay una diferencia conceptual con los sistemas 
@@
 
-En un sistema distribuido, tener muchísimos branches es sencillo, de hecho 
-es más que sencillo, es "natural". Lo que permite un sistema distribuido es 
-no solo tener branches baratos sino también simplificar los merges.
+%En un sistema distribuido, tener muchísimos branches es sencillo, de hecho 
+%es más que sencillo, es "natural". Lo que permite un sistema distribuido es 
+%no solo tener branches baratos sino también simplificar los merges.
 

### 2010-04-25 paper.tex
agregue algo de performance

@@
 
+\subsection{Performance}
+
 Operations being done offline also means that there is no network latency to be worried of,
@@
 system is too slow, it might affect the workflow of the tool. Operations like commits, 
-searching through the history, taking the diff out of two branches,  
+searching through the history, taking the diff out of two branches, and especially merging
+if not done fast enough are limiting what you can do with it, the impact of this depending of 
+the size of the repository.
 % Explicaremos el principio de funcionamiento de la herramienta distribuida 

### 2010-04-25 paper.tex
add branch, tag and merge

--- 2010-04-25 paper.tex
@@
 
-Operations being done offline also means that there is no network latency to be worried of,
-and can be more performant. Performance is important in VCS because if the revision
-system is too slow, it might affect the workflow of the tool. Operations like commits, 
-searching through the history, taking the diff out of two branches,  
 % Explicaremos el principio de funcionamiento de la herramienta distribuida 
@@
 In a centralized VCS, most of the time commits aren't done until you are sure that 
-the change is well tested and can be actually shared to everybody else, since the 
-commit is going to be shared as soon as it's done, and could ``break the build''. 
-In a DVCS the nature of the commits change, since commits are made in the local 
-repository, they tend to be more atomic, 
+the change is well written and can be actually shared to everybody else, since the 
+commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
+change, since commits are made in the local repository, they tend to be more atomic, 
 and commits aren't huge changesets but can be logical, coherent changes.
@@
 so this is not always done.
-
 %En el sistema distribuido, hay una diferencia conceptual con los sistemas 
@@
 
-\subsection{Branching and Merging}
+\subsection{Tagging and Branching}
 
@@
 
+Centralized VCS's like Subversion makes certain copies through history called tags.
+But on Git we have more tools, one of them is that we can have an arbitrary description attached in the tag, in fact, you can store the whole release announcements here.
+Moreover, as with the commit, is stored the identity of who made the tag and this identity can be verified if we add a cryptographically PGP sign to the tag
+
+\subsection{Merging}
+
+Merge on Git between branches is great!, all the history of both branches is preserved over the merges.
+When we make a merge we have two scenarios:
+Fast-forward merge: we refer to this when the changes only was made on only one of the branches, they are simply replayed on the other branch.
+Three-way merge: When changes exists on both branches, they are merged and git will report any conflict and let you resolve them.
+
 \subsection{Pushing and fetching/pulling}
 
-Estos dos conceptos son distintos al check in / check out centralizado, 
-consisten en el envío o recepción de commits entre dos repositorios. Aquí 
-explicaremos un poco en que consisten y cuando hay que usar uno u otro.
+When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
+Push refers to taking all my changes and add them to the repository of another co-worker.
+But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
+Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
+At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.
+
+%Estos dos conceptos son distintos al check in / check out centralizado, 
+%consisten en el envío o recepción de commits entre dos repositorios. Aquí 
+%explicaremos un poco en que consisten y cuando hay que usar uno u otro.
 

### 2010-04-25 paper.tex
cambie unos detalles de lo que subio bruno pa que compile

@@
 
-When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
+When we want to share our work with the rest of the team we have two basic concepts, Push and Pull
 Push refers to taking all my changes and add them to the repository of another co-worker. 
-But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
-Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
-At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.
+But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, 
+instead it, we make Push in a "central repository" where all team make their Pushes too, 
+this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
+lot of "central repositorys" for different parts of our project.
+Pull is a compose action of fetch + merge, where fetch takes the changes from selected 
+repository of a co-worker and copy them to my local repository, merge obiously merges those 
+changes with the sourcecode of my local repository
+At the same way, another co-worker can do Pull over my working copy and get my new code and 
+changes without any problem.
 

### 2010-04-27 paper.tex
Agregue algunas cositas en todas las secciones. Casi como que esta para entregarlo como primera iteracion

--- 2010-04-25 paper.tex
@@
 %----------------------------------------------------------------------
-\title[Investigation on GIT]{%
-       Investigation on GIT}
+\title[Distributed Version Control Systems]{%
+       Distributed Version Control Systems}
 
@@
 % commands).
-\author[GRUPOAPIT]{Damian Alonso,%
-\and{} Bruno Bonnano
+\author[GRUPOAPIT]{Damian Alonso,
+\and{} Bruno Bonnano,
 \and{} Nicol\'{a}s Calligaro
@@
 the license to use BitKeeper was finished. 
-To replace the use of BitKeeper in the Linux kernel, two projects started, Git and 
+To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
+Linus Torvalds \cite{linusgit} and 
 Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
@@
 
-Ejemplo de cita \cite{linusgit}
+%Ejemplo de cita \cite{linusgit}
 
@@
 
-\subsection{Atomic Commits}
+\subsection{More Atomical Commits}
 
@@
 and commits aren't huge changesets but can be logical, coherent changes. 
+Many little commits, if needed, can be grouped as a bigger, conceptual commit.
 To do this in a centralized VCS, one would have to create a new branch of the source code, 
@@
 so this is not always done.
+Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
+which consists of ``picking'' what changes you want to use in a version, and build 
+a new version containing only those changes. This way the revision tree is seen as a 
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions
+(this also makes commits easier).
+
 %En el sistema distribuido, hay una diferencia conceptual con los sistemas 
@@
 Centralized VCS's like Subversion makes certain copies through history called tags. 
-But on Git we have more tools, one of them is that we can have an arbitrary description attached in the tag, in fact, you can store the whole release announcements here.
-Moreover, as with the commit, is stored the identity of who made the tag and this identity can be verified if we add a cryptographically PGP sign to the tag
+But on Git we have more tools, one of them is that we can have an arbitrary 
+description attached in the tag, in fact, you can store the whole release announcements here. 
+Moreover, as with the commit, is stored the identity of who made the tag and this identity 
+can be verified if we add a cryptographically PGP sign to the tag.
 
@@
 
-Merge on Git between branches is great!, all the history of both branches is preserved over the merges.
+Merge on Git between branches is greatly improved over, say, SVN, because all the history of 
+both branches is preserved over the merges.
 When we make a merge we have two scenarios:
-Fast-forward merge: we refer to this when the changes only was made on only one of the branches, they are simply replayed on the other branch.
-Three-way merge: When changes exists on both branches, they are merged and git will report any conflict and let you resolve them.
+Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
+they are simply replayed on the other branch.
+Three-way merge: When changes exists on both branches, they are merged and git will report any 
+conflict and let you resolve them.
 
-\subsection{Pushing and fetching/pulling}
+\subsection{Pushing and pulling}
 
-When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
-Push refers to taking all my changes and add them to the repository of another co-worker.
-But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
-Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
-At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.
+% comentario via nps: cambié ``co-worker'' por ``peer'' porque es más neutral
+When we want to share our work with the rest of the team we have two basic concepts, 
+\emph{push} and \emph{pull}.
+Push refers to taking all my changes and add them to the repository of another peer. 
+But in practice we don't do this becouse we shouldn't make a push on a peer working copy, 
+instead it, we push in a ``central repository'' where all the team make their pushes too, 
+this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
+lot of ``central repositories'' for different parts of our project.
+Pull is a composite action of ``fetch'' and ``merge'', fetching takes the changes from selected 
+repository of a peer and copies them to a local repository, and 
+then those changes are merged with the sourcecode of my local repository.
+In the same way, another peer can pull on my working copy and get my code and 
+changes without any problem.
+
+If you work against a central repository, pulling and pushing do look very much like
+the idea of checking out and checking in, but that's the only way of working in a centralized VCS.
+In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
+read-only mode (via ssh, http, or just sharing the directory) to let other people pull from them.
 
@@
 
-Explicar los casos donde resulta interesante aplicar esta herramienta. 
-También la idea es mostrar configuraciones posibles para la empresa donde 
-se vea la forma de hacer cosas que con un sistema no distribuido no sería 
-posible, o como es posible hacer lo mismo que se podía hacer con svn 
-(usando un repositorio que tenga el branch principal), de manera que 
-no te limita.
+As mentioned before, this tool allows for differents workflows that just weren't 
+possible before.
+
+Changes can be just shared between peers, without needing to access the central 
+repository. Branches can be created instantly, and merging them is easier since 
+the whole history of changesets is preserved instead of just taking the diff of 
+the versions.
+
+Push and pull are much more versatile than checking in and out, since you can push 
+changes into many repositories and pull from many others, not just a central one.
+In fact, there is no need to push at all:
+everyone could be just pulling changes from each other. For example, two co-workers could work 
+in a feature, pulling from each other, then let a third one fetch them and do a code review, and then 
+discard it or merge it. A fourth could fetch all reviewed changes into a test version, to do an 
+acceptance test, and then merge the changes into a final version.
+
+%Explicar los casos donde resulta interesante aplicar esta herramienta. 
+%También la idea es mostrar configuraciones posibles para la empresa donde 
+%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
+%posible, o como es posible hacer lo mismo que se podía hacer con svn 
+%(usando un repositorio que tenga el branch principal), de manera que 
+%no te limita.
 
@@
 \section{Then, why should I use it in my project?}
+Does everybody need these features? Speed, offline working, 
+and easyness of branching/merging are nice features even if you work simply pulling 
+and pushing changes against a central repository and not every peer out there. In some 
+projects and with some tools, the advantage of going distributed may not be clear. 
+For starters, in many closed source projects there is no need nor desire to have anything
+other than centralized repositories, and while you can use a DVCS with a centralized
+repository, there may not be enough to gain to balance the cost of changing. Distributed 
+versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
+of it, even if most of the time you can ignore most features and use just what you need 
+(even for one person proyects, Git and Mercurial may be easier to use than SVN).
+Centralized VCS also have their advantages, you don't need to have the whole history in your 
+personal repository so you can save space, for example in Perforce you can check out only a part of the 
+repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
+without getting a performance hit on some operations\cite{linusgit}.
 
-Explicar los casos donde resulta interesante aplicar esta herramienta. 
-También la idea es mostrar configuraciones posibles para la empresa donde 
-se vea la forma de hacer cosas que con un sistema no distribuido no sería 
-posible, o como es posible hacer lo mismo que se podía hacer con svn 
-(usando un repositorio que tenga el branch principal), de manera que 
-no te limita.
+%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
+%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
+% siempre desde el punto de vista "closed source" (debatible).
 
@@
 Linus Torvalds
-\newblock Google Talk presentation on Git
+\newblock \emph{Google Talk presentation on Git}
+
+\bibitem{perforceclientspec}
+Perforce documentation on ``Editing Client Specs''
+
+\newblock \emph{
+http://www.perforce.com/perforce/doc.current/manuals/p4web
+/help/editclient.html
+}
 

### 2010-04-27 paper.tex
Agregue un comentario sobre el soporte de las herramientas y plugines

@@
 
+Another issue with these systems is that the tool support and various plugins just isn't as 
+mature as systems like SVN, which are much more mature in that regard. Git, in particular, is 
+biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
+Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
+to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
+easing transitions.
+
 %Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 

### 2010-04-27 paper.tex
Corregida una frase en la introducción de Architecture
Modificada la introducción de More Atomical Commits para que quede más en ingles :)

@@
 In a DVCS like Git, everybody has the full repository in their hard drives.
-Since there is no central server, operations on the repository all are done 
+Since there is no central server, all the operations on the repository are done 
 offline. This means that actions like commiting do not depend on having a 
@@
 commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
-change, since commits are made in the local repository, they tend to be more atomic, 
-and commits aren't huge changesets but can be logical, coherent changes. 
+is different, since commits are made in the local repository only. Therefore, they can be more atomic, 
+because commits aren't huge changesets but can be logical, coherent and smaller changes.
+
 Many little commits, if needed, can be grouped as a bigger, conceptual commit.

### 2010-04-27 paper.tex
Modificada otras oraciones en More Atomical Commits

@@
 To do this in a centralized VCS, one would have to create a new branch of the source code, 
-and then merge the branch, but creating and merging branches all the time is 
-not effortless, and branches are seen by everybody that can access the repository, 
+and then merge the branch back to the trunk. But creating and merging branches all the time is 
+not effortless, and branches can be seen by everybody that has access to the repository, 
 so this is not always done.
+
 Doing logical commits allows you to do apply a technique called ``cherry-picking'', 

### 2010-04-27 paper.tex
Sección Tagging and Branching corregida un poquito.

@@
 Centralized VCS's like Subversion makes certain copies through history called tags. 
-But on Git we have more tools, one of them is that we can have an arbitrary 
-description attached in the tag, in fact, you can store the whole release announcements here. 
-Moreover, as with the commit, is stored the identity of who made the tag and this identity 
-can be verified if we add a cryptographically PGP sign to the tag.
+On Git we have more tools, with one of them you can have an arbitrary 
+description attached in the tag. In fact, you can store the whole release announcements there. 
+Moreover, as with the commit, the identity of who made the tag is stored and this identity 
+can be securely verified if we add a cryptographically PGP sign to the tag.
 

### 2010-04-27 paper.tex
Quite el ", say," porque suena a demasiado informal con respecto al resto del paper.
Agregue la subseccion "Peer code review"

@@
 
-Merge on Git between branches is greatly improved over, say, SVN, because all the history of 
+Merge on Git between branches is greatly improved over SVN, because all the history of 
 both branches is preserved over the merges.
@@
 %----------------------------------------------------------------------
+%Explicar los casos donde resulta interesante aplicar esta herramienta. 
+%También la idea es mostrar configuraciones posibles para la empresa donde 
+%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
+%posible, o como es posible hacer lo mismo que se podía hacer con svn 
+%(usando un repositorio que tenga el branch principal), de manera que 
+%no te limita.
+
 \section{Should I use it in my project?}
@@
 
-%Explicar los casos donde resulta interesante aplicar esta herramienta. 
-%También la idea es mostrar configuraciones posibles para la empresa donde 
-%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
-%posible, o como es posible hacer lo mismo que se podía hacer con svn 
-%(usando un repositorio que tenga el branch principal), de manera que 
-%no te limita.
+\subsection{Peer code review}
+If doing code review is a common practice, then using a DVCS can aid to this process. Since changes can be shared
+among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be
+working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the
+reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
+This also prevented them from sharing the code through a public repository, which can present some disadvantages like
+a third developer using code that is not yet intended for general use.
+
+After the review, they can push changes to some public repository for everyone to use, or the reviewer can push changes to the reviewee repository for further fixes.
+All of this is completely isolated from the rest of the team and with no commit history loose.
 
@@
 %----------------------------------------------------------------------
+%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
+%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
+% siempre desde el punto de vista "closed source" (debatible).
 \section{Then, why should I use it in my project?}
@@
 easing transitions.
-
-%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
-%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
-% siempre desde el punto de vista "closed source" (debatible).
 

### 2010-04-27 paper.tex
Agregue otra sección a "Should I use it in my project?"

@@
 \newcommand{\latexiie}{\LaTeX2{\Large$_\varepsilon$}}
-
+\usepackage{graphicx}
 %\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
@@
 
+\subsection{Independent subteams}
+If the application being developed requires a large amount of people working at the same time, it is very likely that they are working on different subsystems.
+Each subteam can be working on a different repository, and so the chances of one team messing with the other teams build is completely removed.
+This helps each team to mantain their own build and if a problem on the build arises, then it is something to be solved between a reduced group of people.
+
+Then both repositories can be merged togheter into an integration one by pulling from each of them.
+If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved.
+Then this team con clone the integration repository and merge it with its working repository.
+They can ask the person in charge to pull the changes back again.
+
 %----------------------------------------------------------------------

### 2010-05-16 paper.tex
Renombrada la seccion Should I use it in my project
Mi nombre estaba mal escrito :(
modificada introduccion y agregada seccion de historia

@@
 
-%It is given that, in these times, modern software projects need a tool to 
-%automatically track changes made in the source files, called Version Control Systems (VCS).
+% Un detalle que yo corregiría es la Introducción, creo que se  mezclan cosas con diferente 
+% nivel de detalle, entonces propondría hacer una intro de muy alto nivel, que se concentre 
+% en contar el problema y describir el objetivo del artículo.
+% Por otro lado la reseña histórica iría en una sección aparte.
 
-\PARstart Version Control Systems (VCS) usually track the whole history of the
-source code in a central server that everyone that can access. This 
-central server contains all the changes and branches of the code and 
-the users that can read the versions or commit changes have to connect 
-to this repository. The most popular today example of this approach is SVN, which is a 
-widely used VCS.
+\PARstart Most software projects use Version Control Systems (VCS) to manage revisions
+of source code. 
+Version Control Systems traditionally track the whole history of the
+source code in a central server that everyone that can access. 
+%This central server contains all the changes and branches of the code and 
+%the users that can read the versions or commit changes have to connect 
+%to this repository. 
+Users need to access this central server to work with their VCS.
+A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
+In these systems, there is no central server that contains the history and tracks changes,
+instead everyone has a copy of the full repository with the complete history.
+Given the lack of a centralized server they are also called De-centralized Version Control Systems.
 
-Distributed Version Control Systems (DVCS) are a modern way of managing
-revisions of software that do not have a centralized server, for this reason 
-they are also called De-centralized Version Control Systems. Everybody has a 
-copy of the full repository with all changes made in the history.
+In this paper we're going explain what DVCS are, based on the distributed system Git, 
+and compare them to centralized Version Control Systems,
+highlighting the differences, advantages and disadvantages of both approachs in various 
+contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
+evaluating when to use or not Distributed Version Control Systems.
 
-The concept of distributed repositories came up first on the commercial product 
-Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
-on to design BitKeeper, another commercial VCS which expanded on those ideas. 
-BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
-the license to use BitKeeper was finished. 
-To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
-Linus Torvalds \cite{linusgit} and 
-Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
-developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
-the idea of tracking only patches and not versions.
+% Explain DVCS, particulary GIT
+% Comparison between DVCS and CVCS
+% When we should or we shouldn't use it.
 
@@
 
-We're going to do a comparison between centralized and decentralized control version systems,
-highlighting the differences and advantages and disadvantages of both approachs in various 
-contexts, both on a conceptual and practical level. In this paper we'll base our explanations 
-on Git but there are no big differences between 
-most of these DVCS, especially between Git and Mercurial that are largely similar, with 
-most commands having the same names in both tools.
-
 %La idea del paper sería contar las ventajas que puede 
@@
 %Ejemplo de cita \cite{linusgit}
+
+\section{DVCS history}
+
+The concept of distributed repositories came up first on the commercial product 
+Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
+on to design BitKeeper, another commercial VCS which expanded on those ideas. 
+BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
+the license to use BitKeeper was finished. 
+To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
+Linus Torvalds \cite{linusgit} and Mercurial, both now mature DVCS. 
+Other open source DVCS in use today are Bazaar, 
+developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
+the idea of tracking only patches and not versions.
+
+For reference, in this paper we'll base our explanations on Git but for most features there 
+are no big differences between most of these DVCS, especially between Git and Mercurial which are 
+largely similar, with most commands having the same names in both tools.
 

### 2010-05-16 paper.tex
Nueva sección Centralized repository with integration manager

--- 2010-04-27 paper.tex
@@
 % commands).
-\author[GRUPOAPIT]{Damian Alonso,
+\author[GRUPOAPIT]{Demian Alonso,
 \and{} Bruno Bonnano,
@@
 
-\section{Should I use it in my project?}
+\section{Possible workflows}
 
@@
 If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved.
-Then this team con clone the integration repository and merge it with its working repository.
+Then this team can clone the integration repository and merge it with its working repository.
 They can ask the person in charge to pull the changes back again.
+
+\subsection{Centralized repository with integration manager}
+It is possible to have a single central repository where all developers have read access.
+Everyone has an official public version from which they can work from.
+Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed.
+When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
 

### 2010-05-16 paper.tex
Extendida la seccion Centralized repository with integration manager
agregada seccion de comparativa

--- 2010-05-16 paper.tex
@@
 
+\section{Comparison}
+
+\subsection{Commits}
+In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
+Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
+DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.
+
+Also, DVCS allow to apply a technique called ``cherry-picking'', 
+which consists of ``picking'' what changes you want to use in a version, and build 
+a new version containing only those changes. This way the revision tree is seen as a 
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+
 %Estos dos conceptos son distintos al check in / check out centralizado, 

### 2010-05-16 paper.tex

--- 2010-05-16 paper.tex
@@
 When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
+It is also possible to have an automatic integration manager.
+This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository.
+Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
 

### 2010-05-16 paper.tex
Re-escritura de Architecture basado en 'no comparar' con svn

--- 2010-05-16 paper.tex
@@
 % commands).
-\author[GRUPOAPIT]{Demian Alonso,
+\author[GRUPOAPIT]{Damian Alonso,
 \and{} Bruno Bonnano,
@@
 \section{Architecture}
+
+A DVCS has many features that makes it perfect for distributed and non-distributed developments.
+Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
+
+\subsection{Distributed}
+The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited.
+This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes.
+It also makes the whole versioning system faster.
+
+\subsection{Change-sets}
+You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a co-worker's repository for instance, and pull some changes from another co-worker to your local clone.
+To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
+
+\subsection{Patchs}
+The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit.
+You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.
+
+\subsection{Flexibility}
+If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
+This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.
+
+\subsection {Distributed Repository}
 
@@
 
-\section{Possible workflows}
+\section{Should I use it in my project?}
 
@@
 If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved.
-Then this team can clone the integration repository and merge it with its working repository.
+Then this team con clone the integration repository and merge it with its working repository.
 They can ask the person in charge to pull the changes back again.
-
-\subsection{Centralized repository with integration manager}
-It is possible to have a single central repository where all developers have read access.
-Everyone has an official public version from which they can work from.
-Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed.
-When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
 
@@
 %----------------------------------------------------------------------
+\section{Glossary}
+{\renewcommand{\labelitemi}{$\triangleright$}
+\begin{itemize}
+\item CVS
+\item Centralized CVS
+\item Distributed/de-centralized CVS
+\end{itemize}
 

### 2010-05-16 paper.tex

@@
 If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved.
-Then this team con clone the integration repository and merge it with its working repository.
+Then this team can clone the integration repository and merge it with its working repository.
 They can ask the person in charge to pull the changes back again.
+
+\subsection{Centralized repository with integration manager}
+It is possible to have a single central repository where all developers have read access.
+Everyone has an official public version from which they can work from.
+Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed.
+When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
+It is also possible to have an automatic integration manager.
+This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository.
+Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
 

### 2010-05-16 paper.tex
Expanded Centralized repository with integration manager

--- 2010-05-16 paper.tex
@@
 
+In case the number of developers is really big (for instance on an OpenSource project) then a single person cannot deal with the integration from all of them.
+Then a hierarchycal approach can be taken and there will be a level of integrators who are responsable for merging all the changes from a particular subsystem.
+A main integrator will merge all the changes from the subsystem's integrator to create and publish the public version.
+
 %----------------------------------------------------------------------

### 2010-05-16 paper.tex
agregadas secciones de comparison: merging y sharing changes

@@
 
-If you work against a central repository, pulling and pushing do look very much like
-the idea of checking out and checking in, but that's the only way of working in a centralized VCS.
-In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
-read-only mode (via ssh, http, or just sharing the directory) to let other people pull from them.
-
 \section{Comparison}
@@
 series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+
+\subsection{Merging}
+Merging on Git between branches is greatly improved over SVN, because all the history of 
+both branches is preserved over the merges. %agregar citation
+
+\subsection{Sharing changes}
+If you work simply pulling and pushing against a central repository, those operations do look 
+very much like the operations idea of check out and check in in a centralized VCS, 
+but that's the only way of sharing changes in a centralized VCS.
+In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
+read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
 
@@
 Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
-
-In case the number of developers is really big (for instance on an OpenSource project) then a single person cannot deal with the integration from all of them.
-Then a hierarchycal approach can be taken and there will be a level of integrators who are responsable for merging all the changes from a particular subsystem.
-A main integrator will merge all the changes from the subsystem's integrator to create and publish the public version.
 

### 2010-05-16 paper.tex
Seccion de Architecture casi terminada

--- 2010-05-16 paper.tex
@@
 
-In a DVCS like Git, everybody has the full repository in their hard drives.
-Since there is no central server, all the operations on the repository are done 
-offline. This means that actions like commiting do not depend on having a 
-network connection, since commits are made on your repository.
+A DVCS has many features that makes it perfect for distributed and non-distributed developments.
+Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
 
-Changes can thus be shared between everyone passing changes between repositories, 
-without the need of making those changes in a central repository.
+\subsection{Distributed}
+The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited.
+This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes.
+It also makes the whole versioning system faster.
 
-% Explicaremos el principio de funcionamiento de la herramienta distribuida 
-% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
-% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
-% su propio repositorio, que las versiones pueden ser infinitas (por más que 
-% haya una(s) maestra(s)), que se puede trabajar offline, etc.
+\subsection{Change-sets}
+You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
+To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
 
-% -habria que agregar una imagen de muetsra
+\subsection{Patchs}
+The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit.
+You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.
 
-\subsection{More Atomical Commits}
+\subsection{Flexibility}
+If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
+This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.
 
-In a centralized VCS, most of the time commits aren't done until you are sure that 
-the change is well written and can be actually shared to everybody else, since the 
-commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
-is different, since commits are made in the local repository only. Therefore, they can be more atomic, 
-because commits aren't huge changesets but can be logical, coherent and smaller changes.
+\subsection{Trust Based Security}
+Security on DVCS is based on the "circle of trust" model which implies that you trust only on a very specific group of people and you only pull from those people which in turn trust in their own group of people and only pull from that other group of people.
+This creates a chain of trust so that even if you don't trust some one directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.
 
-Many little commits, if needed, can be grouped as a bigger, conceptual commit.
-To do this in a centralized VCS, one would have to create a new branch of the source code, 
-and then merge the branch back to the trunk. But creating and merging branches all the time is 
-not effortless, and branches can be seen by everybody that has access to the repository, 
-so this is not always done.
-
-Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
-which consists of ``picking'' what changes you want to use in a version, and build 
-a new version containing only those changes. This way the revision tree is seen as a 
-series of \emph{changesets} or \emph{patches} instead of just a series of static versions
-(this also makes commits easier).
-
-%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
-%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
-%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
-%entonces no hay preocupaciones como romper el build.
+\subsection{Small, Coherent and Logical Commits}
+Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code.
+This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code.
+Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.
 
 \subsection{Tagging and Branching}
-
-%En un sistema distribuido, tener muchísimos branches es sencillo, de hecho 
-%es más que sencillo, es "natural". Lo que permite un sistema distribuido es 
-%no solo tener branches baratos sino también simplificar los merges.
-
-Centralized VCS's like Subversion makes certain copies through history called tags. 
-On Git we have more tools, with one of them you can have an arbitrary 
-description attached in the tag. In fact, you can store the whole release announcements there. 
-Moreover, as with the commit, the identity of who made the tag is stored and this identity 
-can be securely verified if we add a cryptographically PGP sign to the tag.
+Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version.
+Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag
 
 \subsection{Merging}
-
-Merge on Git between branches is greatly improved over SVN, because all the history of 
-both branches is preserved over the merges.
-When we make a merge we have two scenarios:
-Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
-they are simply replayed on the other branch.
-Three-way merge: When changes exists on both branches, they are merged and git will report any 
-conflict and let you resolve them.
+The merging process has two possible scenarios:
+\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
+\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
+The merging process\cite{svnmerging} between branches preserves all the history of 
+both branches on many DVCS tools.
 
 \subsection{Pushing and pulling}
+When we want to share our work with the rest of the team we have two basic commands, 
+\emph{push} and \emph{pull}.
 
-% comentario via nps: cambié ``co-worker'' por ``peer'' porque es más neutral
-When we want to share our work with the rest of the team we have two basic concepts, 
-\emph{push} and \emph{pull}.
-Push refers to taking all my changes and add them to the repository of another peer. 
-But in practice we don't do this becouse we shouldn't make a push on a peer working copy, 
-instead it, we push in a ``central repository'' where all the team make their pushes too, 
-this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
-lot of ``central repositories'' for different parts of our project.
-Pull is a composite action of ``fetch'' and ``merge'', fetching takes the changes from selected 
-repository of a peer and copies them to a local repository, and 
-then those changes are merged with the sourcecode of my local repository.
-In the same way, another peer can pull on my working copy and get my code and 
-changes without any problem.
+\subsection{Pushing}
+The push process refers to taking all the changes previously selected and adding them to the repository of another peer.
+In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too.
+This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team.
+Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.
+
+\subsection{Pulling}
+Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''.
+The fetch command takes the changes from a peer's repository and copies them to the local repository.
+After that, the merge process combines the changes you've just downloaded with the ones on your local repository.
+You can do those two actions separately or altogether by using the ``pull'' command.
 
@@
 series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
-
-\subsection{Merging}
-Merging on Git between branches is greatly improved over SVN, because all the history of 
-both branches is preserved over the merges. %agregar citation
-
-\subsection{Sharing changes}
-If you work simply pulling and pushing against a central repository, those operations do look 
-very much like the operations idea of check out and check in in a centralized VCS, 
-but that's the only way of sharing changes in a centralized VCS.
-In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
-read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
 
@@
 
+\bibitem{svnmerging}
+\newblock \emph{ Git-SVN Crash Course}
+
+\newblock \emph{http://git.or.cz/course/svn.html#merge}
 \end{thebibliography}

### 2010-05-16 paper.tex
movida seccion para la parte de conclusiones
Reescrita la primer oración de Peer code review

--- 2010-05-16 paper.tex
@@
 \subsection{Peer code review}
-If doing code review is a common practice, then using a DVCS can aid to this process. Since changes can be shared
-among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be
-working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the
-reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
-This also prevented them from sharing the code through a public repository, which can present some disadvantages like
-a third developer using code that is not yet intended for general use.
+Using a DCVS can help isolate the code review between both developers without disrupting the rest of the team.
+Since changes can be shared among any workstation, the reviewer can fetch the changes from the reviewee's workstation.
+The reviewer might be working on some other feature and may have it's workspace in an unstable state.
+But this is not a problem since the reviewer can just clone the reviewee's repository and can have it separately from its current changes.
+This also prevented them from sharing the code through a public repository, which can present some disadvantages like a third developer using code that is not yet intended for general use.
 

### 2010-05-16 paper.tex
ahi esta corregi error

--- 2010-05-16 paper.tex
@@
 
+\subsection{Merging}
+Merging on Git between branches is greatly improved over SVN, because all the history of 
+both branches is preserved over the merges. %agregar citation
+
+\subsection{Sharing changes}
+If you work simply pulling and pushing against a central repository, those operations do look 
+very much like the operations idea of check out and check in in a centralized VCS, 
+but that's the only way of sharing changes in a centralized VCS.
+In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
+read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
+
+\subsection{Repository Size}
+
+Centralized VCS also have their advantages, you don't need to have the whole history in your 
+personal repository so you can save space, for example in Perforce you can check out only a part of the 
+repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
+without getting a performance hit on some operations\cite{linusgit}.
+
 %Estos dos conceptos son distintos al check in / check out centralizado, 
@@
 %----------------------------------------------------------------------
+
+%----------------------------------------------------------------------
+% SECTION VII: Conclusions
+%----------------------------------------------------------------------
+\section{Conclusion}
+
 %Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
@@
 % siempre desde el punto de vista "closed source" (debatible).
-\section{Then, why should I use it in my project?}
+\subsection{why should I use it in my project?}
 Does everybody need these features? Speed, offline working, 
@@
 (even for one person proyects, Git and Mercurial may be easier to use than SVN).
-Centralized VCS also have their advantages, you don't need to have the whole history in your 
-personal repository so you can save space, for example in Perforce you can check out only a part of the 
-repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
-without getting a performance hit on some operations\cite{linusgit}.
 
@@
 easing transitions.
-
-%----------------------------------------------------------------------
-% SECTION VII: Conclusions
-%----------------------------------------------------------------------
-\section{Conclusion}
-
-\emph{to be done}
 

### 2010-05-17 paper.tex
Faltaba escapar el # en la bibliografia
desarrollado algo de la conclusion

@@
 
-%Estos dos conceptos son distintos al check in / check out centralizado, 
-%consisten en el envío o recepción de commits entre dos repositorios. Aquí 
-%explicaremos un poco en que consisten y cuando hay que usar uno u otro.
+\subsection{Tool support}
+%the idea here is to explain a bit the state of the art in the toolchain support
+%eclipse plugins, tortoisegit 'n tortoisehg, etc.
+
+With these DVCS, tool support and various plugins just isn't as 
+mature as systems like SVN, which are more mature and well tested. 
+Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
+Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
+to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
+easing transitions.
 
 %----------------------------------------------------------------------
-% SECTION III: Should I use it in my project?
-%----------------------------------------------------------------------
-%Explicar los casos donde resulta interesante aplicar esta herramienta. 
-%También la idea es mostrar configuraciones posibles para la empresa donde 
-%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
-%posible, o como es posible hacer lo mismo que se podía hacer con svn 
-%(usando un repositorio que tenga el branch principal), de manera que 
-%no te limita.
 
@@
 % siempre desde el punto de vista "closed source" (debatible).
-\subsection{why should I use it in my project?}
+%\subsection{Should I use it in my project?}
 Does everybody need these features? Speed, offline working, 
@@
 
-Another issue with these systems is that the tool support and various plugins just isn't as 
-mature as systems like SVN, which are much more mature in that regard. Git, in particular, is 
-biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
-Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
-to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
-easing transitions.
+The general lack of maturity in the tools is also a disadvantage, since the most flexible
+way of working is the command-line interface. This makes it a bit harder to use because there 
+are many commands, and they have a lot of options and some problems may not have an intuitive 
+solution. There is more to learn and to use.
+
+If there is no need to use anything but a centralized workflow, as in Continous Integration 
+workflows, there might be little justification to use DVCS because changes are supposed to be 
+integrated quickly in the main repository.
+
+Beside these general warnings, Distributed VCS is simply more powerful and flexible than Centralized CVS.
+Everything that can be done with a centralized schema can be done in a distributed fashion, but the inverse
+is not true.
 
@@
 
-\newblock \emph{http://git.or.cz/course/svn.html#merge}
+\newblock \emph{http://git.or.cz/course/svn.html\#merge}
 \end{thebibliography}

### 2010-05-18 paper.tex
Agregadas algunas imagenes
Se agrego el apartado del repositorio centralizado

@@
 \usepackage{graphicx}
+
+\newcommand{\diagrama}[1]{\begin{center}
+    \includegraphics[width=.8\linewidth, keepaspectratio]{#1} 
+\end{center}}
+
 %\usepackage{ieeetsp}	% if you want the "trans. sig. pro." style
@@
 
+\diagrama{PeerCodeReview.jpg}
+
+\subsection{Centralized server}
+The classic workflow where there is one central server which has the whole project is also available.
+In this case all developers has access to the server and can pull and push changes from it.
+The main advantages is that any developer can share changes among other developer without needing to use the central server.
+However once a piece of code is considered finished it should be pushed to this server.
+
+\diagrama{RepoCentral.jpg}
+
 \subsection{Independent subteams}
@@
 
+\diagrama{IndependentSubteams.jpg}
 \subsection{Centralized repository with integration manager}
@@
 Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
+
+\diagrama{ResponsableIntegracion.jpg}
 

### 2010-05-18 paper.tex
Added a caption to all images

@@
 
-\newcommand{\diagrama}[1]{\begin{center}
+\newcommand{\diagrama}[2]{
+    \begin{figure}[h]
+        \begin{center}
             \includegraphics[width=.8\linewidth, keepaspectratio]{#1} 
-\end{center}}
+        \end{center}
+        \caption{#2}
+    \end{figure}
+}
 
@@
 
-\diagrama{PeerCodeReview.jpg}
+\diagrama{PeerCodeReview.jpg}{Peer Code Review workflow}
 
-\subsection{Centralized server}
+\subsection{Centralized Server}
 The classic workflow where there is one central server which has the whole project is also available.
@@
 
-\diagrama{RepoCentral.jpg}
+\diagrama{RepoCentral.jpg}{Centralized Server workflow}
 
@@
 
-\diagrama{IndependentSubteams.jpg}
+\diagrama{IndependentSubteams.jpg}{Independent Subteams workflow}
+
 \subsection{Centralized repository with integration manager}
@@
 
-\diagrama{ResponsableIntegracion.jpg}
+\diagrama{ResponsableIntegracion.jpg}{Centralized repository with integration manager workflow}
 

### 2010-06-06 laarsample.tex
template correcto agregado

%\input{tcilatex}

\documentstyle[laarstyle]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TCIDATA{Created=Mon Jun 26 12:16:44 2000}
%TCIDATA{LastRevised=Fri Feb 21 17:20:01 2003}
%TCIDATA{Language=American English}

\affiliation{
\dag Chemical Engng. Department, Caltech, Pasadena, CA 91125, USA \\
{\ xalpha@caltech.edu} \\
\ddag Dto. de Ing. Mec\'{a}nica, Univ. Nac. del Litoral, 7500 Santa Fe
, Argentina \\
{\ ybetha@intec.edu.ar}
}
%\input{tcilatex}
\begin{document}

\title{CAMERA-READY INSTRUCTIONS (LAAR)}
\author{X. X. ALPHA$^{\dag }$ and Y. Y. BETHA$^{\ddag }$}
\maketitle

\abstract
These instructions are presented to assist authors in preparing a typescript
which is suitable for direct photo-offset reproduction. The abstract should
not exceed 200, 150 and 50 words for Review Papers, Articles and Notes
respectively.\endabstract

%TCIMACRO{\TeXButton{keywords}{\keywords}}
%BeginExpansion
\keywords%
%EndExpansion
Up to five keywords should be provided.\endkeywords

\section{INTRODUCTION}

The authors are fully responsible for the printing quality of their papers,
and are kindly requested to observe carefully the following instructions for
the preparation of their manuscripts. This document is itself an example of
the desired layout for camera-ready papers.

There is no limit to the length of the paper. However, it is recommended
that Review Papers, Articles and Notes do not exceed 10, 8, and 4 pages,
respectively. The publisher will charge a mandatory page charge of US\$ 75
per page for each page in excess of 10, 8 or 4 depending on the type of
contributions.

\section{METHODS}

\subsection{Typing Instructions}

Manuscripts must be typed in a two column format within a box of 165 mm $%
\times $ 245 mm. Column width should be 80 mm with a 5 mm space between both
columns. Authors should send to the Editorial Board a high quality hard copy
(laser printers or letter quality printers should be used) and an electronic
version (in *.pdf or *.ps files) of their revised final version.

\subsection{Font Size and Spacing Lines}

Manuscripts must be typed with single line spacing. Increase line spacing
only when necessary for subscripts and/or superscripts. Font size in text
and any drawings should be, at least, of approximately 2 mm high. The
minimum font size for the body of the text is 10 point (1 point=0.35 mm).

\subsection{Illustrative Materials}

Illustrations must be originals or photographic prints of originals. Arrange
them throughout the paper and do not group them together at the end. Figure
captions must be typed beneath each figure.

Tables can be typed directly onto the sheets. Table headings should be as
brief as possible and typed directly above the table.

The words ``Figure'' and ``Equation'' should be shortened to ``Fig.'' and
``Eq.'' whenever they occur within a sentence. They should, however, be
written in full when they appear at the beginning of a sentence. Equations,
figures and tables must be numbered in Arabic numbers. The number of the
equation should be aligned to the right margin

\begin{equation}
\dot{x}=f_{1}\left( x_{1},t\right) +\alpha x_{2}\sin \left( \theta \right)
\label{eq1}
\end{equation}
and the equation itself should be centered.

\subsection{Format of References}

Within the text, the references should be quoted by author 's surname and
year. Use both authors' surname if two, first author and ``{\it et al.}''
when more than two. Depending on sense, either the year only is placed in
parentheses, or the author's surname and year separated by a comma are
placed together in parentheses as shown below. For example: ``Komatsue
(1977a) discovered...''. ``Recent results (Arnikar {\it et al.}, 1970;
Holland, 1981) indicate...''. ``Komatsue (1977a, b) found...''. ``Early
investigators (Komatsue and Simand, 1987) thought...''. The list of
references should be typed in {\it alphabetical order} and follow the
general style given below as an example.

\section{CONCLUSIONS}

It is important to adhere to these ``rules'' so that the volume can be
produced quickly, efficiently and in a fully appealing readable form.

\begin{thebibliography}{9}
\bibitem{arnikar1965}  Arnikar, H.J., T.S. Rao and A. Bodne, ``A gas
chromatographic study of the kinetics of the uncatalysed esterification of
aceticacid by ethanol,'' {\it J. Chromatog.}, {\bf 47}, 265-268 (1970).

\bibitem{Holland1980}  Holland, C.D., {\it Fundamentals of Multicomponent
Distillation}, McGraw-Hill, New York (1981).

\bibitem{Homatsue1977a}  Komatsue, L., ``Application of the relaxation
method for solving reacting distillation problems,'' {\it J. Chem. Eng. Japan%
}, {\bf 10}, 200-205 (1977a).

\bibitem{Komatsue1977b}  Komatsue, L., ``A new method of convergence for
solving reacting distillation problems,'' {\it J. Chem. Eng. Japan}, {\bf 10}%
, 292-297 (1977b).

\bibitem{Komatsue1987}  Komatsue, L. and J. Simand, ``Simulation of reactive
distillation by the inside-outside method,'' {\it Proc. 37th Chem. Eng. Conf.%
}, Montreal, Canada, 365-367 (1987).
\end{thebibliography}

\end{document}

### 2010-06-06 laarsample.tex
Agrego el formato q pide la catedra

@@
 %\input{tcilatex}
-
-\documentstyle[laarstyle]{article}
+\documentstyle[laarstyle,graphicx,fancyhdr]{article}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\newcommand{\diagrama}[2]{
+    \begin{figure}[h]
+        \begin{center}
+            \includegraphics[width=.8\linewidth, keepaspectratio]{#1} 
+        \end{center}
+        \caption{#2}
+    \end{figure}
+}
+
 \affiliation{
-\dag Chemical Engng. Department, Caltech, Pasadena, CA 91125, USA \\
-{\ xalpha@caltech.edu} \\
-\ddag Dto. de Ing. Mec\'{a}nica, Univ. Nac. del Litoral, 7500 Santa Fe
-, Argentina \\
-{\ ybetha@intec.edu.ar}
+\dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+{\ demianalonso@gmail.com} \\
+\ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+{\ bbonanno@gmail.com} \\
+\dag \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+{\ nicolascalligaro@gmail.com} \\
+\ddag \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+{\ nicolas.perez.santoro@gmail.com }
 }
+
+\pagestyle{fancy}
+
+\fancyhead{}
+
+\renewcommand{\headrulewidth}{0pt}
+\chead{\fancyplain{}{\emph{Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires}}}
+
 %\input{tcilatex}
@@
 
-\title{CAMERA-READY INSTRUCTIONS (LAAR)}
-\author{X. X. ALPHA$^{\dag }$ and Y. Y. BETHA$^{\ddag }$}
+\title{Distributed Version Control Systems}
+\author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
 \maketitle
@@
 \abstract
-These instructions are presented to assist authors in preparing a typescript
-which is suitable for direct photo-offset reproduction. The abstract should
-not exceed 200, 150 and 50 words for Review Papers, Articles and Notes
-respectively.\endabstract
+Estas instrucciones se presentan para ayudar a los autores a preparar su trabajo en el formato definitivo correspondiente a la materia Arquitecturas de Proyectos de IT.
+El resumen no debe exceder las 200 palabras.
+\endabstract
 
@@
 %EndExpansion
-Up to five keywords should be provided.\endkeywords
+Por favor, incluya hasta cinco palabras clave que identifiquen en forma concreta su trabajo.
+\endkeywords
 
@@
 
-The authors are fully responsible for the printing quality of their papers,
-and are kindly requested to observe carefully the following instructions for
-the preparation of their manuscripts. This document is itself an example of
-the desired layout for camera-ready papers.
+Most software projects use Version Control Systems (VCS) to manage revisions
+of source code. 
+Version Control Systems traditionally track the whole history of the
+source code in a central server that everyone that can access. 
+%This central server contains all the changes and branches of the code and 
+%the users that can read the versions or commit changes have to connect 
+%to this repository. 
+Users need to access this central server to work with their VCS.
+A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
+In these systems, there is no central server that contains the history and tracks changes,
+instead everyone has a copy of the full repository with the complete history.
+Given the lack of a centralized server they are also called De-centralized Version Control Systems.
 
-There is no limit to the length of the paper. However, it is recommended
-that Review Papers, Articles and Notes do not exceed 10, 8, and 4 pages,
-respectively. The publisher will charge a mandatory page charge of US\$ 75
-per page for each page in excess of 10, 8 or 4 depending on the type of
-contributions.
+In this paper we're going explain what DVCS are, based on the distributed system Git, 
+and compare them to centralized Version Control Systems,
+highlighting the differences, advantages and disadvantages of both approachs in various 
+contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
+evaluating when to use or not Distributed Version Control Systems.
 
-\section{METHODS}
+\section{DVCS HISTORY}
 
-\subsection{Typing Instructions}
+The concept of distributed repositories came up first on the commercial product 
+Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
+on to design BitKeeper, another commercial VCS which expanded on those ideas. 
+BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
+the license to use BitKeeper was finished. 
+To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
+Linus Torvalds \cite{linusgit} and Mercurial, both now mature DVCS. 
+Other open source DVCS in use today are Bazaar, 
+developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
+the idea of tracking only patches and not versions.
 
-Manuscripts must be typed in a two column format within a box of 165 mm $%
-\times $ 245 mm. Column width should be 80 mm with a 5 mm space between both
-columns. Authors should send to the Editorial Board a high quality hard copy
-(laser printers or letter quality printers should be used) and an electronic
-version (in *.pdf or *.ps files) of their revised final version.
+For reference, in this paper we'll base our explanations on Git but for most features there 
+are no big differences between most of these DVCS, especially between Git and Mercurial which are 
+largely similar, with most commands having the same names in both tools.
 
-\subsection{Font Size and Spacing Lines}
+%----------------------------------------------------------------------
+% SECTION II: Architecture
+%----------------------------------------------------------------------
+\section{ARCHITECTURE}
 
-Manuscripts must be typed with single line spacing. Increase line spacing
-only when necessary for subscripts and/or superscripts. Font size in text
-and any drawings should be, at least, of approximately 2 mm high. The
-minimum font size for the body of the text is 10 point (1 point=0.35 mm).
+A DVCS has many features that makes it perfect for distributed and non-distributed developments.
+Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
 
-\subsection{Illustrative Materials}
+\subsection{Distributed}
+The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited.
+This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes.
+It also makes the whole versioning system faster.
 
-Illustrations must be originals or photographic prints of originals. Arrange
-them throughout the paper and do not group them together at the end. Figure
-captions must be typed beneath each figure.
+\subsection{Change-sets}
+You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
+To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
 
-Tables can be typed directly onto the sheets. Table headings should be as
-brief as possible and typed directly above the table.
+\subsection{Patchs}
+The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit.
+You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.
 
-The words ``Figure'' and ``Equation'' should be shortened to ``Fig.'' and
-``Eq.'' whenever they occur within a sentence. They should, however, be
-written in full when they appear at the beginning of a sentence. Equations,
-figures and tables must be numbered in Arabic numbers. The number of the
-equation should be aligned to the right margin
+\subsection{Flexibility}
+If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
+This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.
 
-\begin{equation}
-\dot{x}=f_{1}\left( x_{1},t\right) +\alpha x_{2}\sin \left( \theta \right)
-\label{eq1}
-\end{equation}
-and the equation itself should be centered.
+\subsection{Trust Based Security}
+Security on DVCS is based on the "circle of trust" model which implies that you trust only on a very specific group of people and you only pull from those people which in turn trust in their own group of people and only pull from that other group of people.
+This creates a chain of trust so that even if you don't trust some one directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.
 
-\subsection{Format of References}
+\subsection{Small, Coherent and Logical Commits}
+Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code.
+This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code.
+Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.
 
-Within the text, the references should be quoted by author 's surname and
-year. Use both authors' surname if two, first author and ``{\it et al.}''
-when more than two. Depending on sense, either the year only is placed in
-parentheses, or the author's surname and year separated by a comma are
-placed together in parentheses as shown below. For example: ``Komatsue
-(1977a) discovered...''. ``Recent results (Arnikar {\it et al.}, 1970;
-Holland, 1981) indicate...''. ``Komatsue (1977a, b) found...''. ``Early
-investigators (Komatsue and Simand, 1987) thought...''. The list of
-references should be typed in {\it alphabetical order} and follow the
-general style given below as an example.
+\subsection{Tagging and Branching}
+Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version.
+Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag
 
-\section{CONCLUSIONS}
+\subsection{Merging}
+The merging process has two possible scenarios:
+\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
+\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
+The merging process\cite{svnmerging} between branches preserves all the history of 
+both branches on many DVCS tools.
 
-It is important to adhere to these ``rules'' so that the volume can be
-produced quickly, efficiently and in a fully appealing readable form.
+\subsection{Pushing and pulling}
+When we want to share our work with the rest of the team we have two basic commands, 
+\emph{push} and \emph{pull}.
+
+\subsection{Pushing}
+The push process refers to taking all the changes previously selected and adding them to the repository of another peer.
+In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too.
+This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team.
+Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.
+
+\subsection{Pulling}
+Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''.
+The fetch command takes the changes from a peer's repository and copies them to the local repository.
+After that, the merge process combines the changes you've just downloaded with the ones on your local repository.
+You can do those two actions separately or altogether by using the ``pull'' command.
+
+\section{COMPARISON}
+
+\subsection{Commits}
+In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
+Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
+DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.
+
+Also, DVCS allow to apply a technique called ``cherry-picking'', 
+which consists of ``picking'' what changes you want to use in a version, and build 
+a new version containing only those changes. This way the revision tree is seen as a 
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+
+\subsection{Merging}
+Merging on Git between branches is greatly improved over SVN, because all the history of 
+both branches is preserved over the merges. %agregar citation
+
+\subsection{Sharing changes}
+If you work simply pulling and pushing against a central repository, those operations do look 
+very much like the operations idea of check out and check in in a centralized VCS, 
+but that's the only way of sharing changes in a centralized VCS.
+In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
+read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
+
+\subsection{Repository Size}
+
+Centralized VCS also have their advantages, you don't need to have the whole history in your 
+personal repository so you can save space, for example in Perforce you can check out only a part of the 
+repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
+without getting a performance hit on some operations\cite{linusgit}.
+
+\subsection{Tool support}
+%the idea here is to explain a bit the state of the art in the toolchain support
+%eclipse plugins, tortoisegit 'n tortoisehg, etc.
+
+With these DVCS, tool support and various plugins just isn't as 
+mature as systems like SVN, which are more mature and well tested. 
+Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
+Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
+to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
+easing transitions.
+
+%----------------------------------------------------------------------
+
+\section{POSSIBLE WORKFLOWS}
+
+As mentioned before, this tool allows for differents workflows that just weren't 
+possible before.
+
+Changes can be just shared between peers, without needing to access the central 
+repository. Branches can be created instantly, and merging them is easier since 
+the whole history of changesets is preserved instead of just taking the diff of 
+the versions.
+
+Push and pull are much more versatile than checking in and out, since you can push 
+changes into many repositories and pull from many others, not just a central one.
+In fact, there is no need to push at all:
+everyone could be just pulling changes from each other. For example, two co-workers could work 
+in a feature, pulling from each other, then let a third one fetch them and do a code review, and then 
+discard it or merge it. A fourth could fetch all reviewed changes into a test version, to do an 
+acceptance test, and then merge the changes into a final version.
+
+\subsection{Peer code review}
+If doing code review is a common practice, then using a DVCS can aid to this process. Since changes can be shared
+among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be
+working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the
+reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
+This also prevented them from sharing the code through a public repository, which can present some disadvantages like
+a third developer using code that is not yet intended for general use.
+
+After the review, they can push changes to some public repository for everyone to use, or the reviewer can push changes to the reviewee repository for further fixes.
+All of this is completely isolated from the rest of the team and with no commit history loose.
+
+\diagrama{PeerCodeReview.jpg}{Peer Code Review workflow}
+
+\subsection{Centralized Server}
+The classic workflow where there is one central server which has the whole project is also available.
+In this case all developers has access to the server and can pull and push changes from it.
+The main advantages is that any developer can share changes among other developer without needing to use the central server.
+However once a piece of code is considered finished it should be pushed to this server.
+
+\diagrama{RepoCentral.jpg}{Centralized Server workflow}
+
+\subsection{Independent subteams}
+If the application being developed requires a large amount of people working at the same time, it is very likely that they are working on different subsystems.
+Each subteam can be working on a different repository, and so the chances of one team messing with the other teams build is completely removed.
+This helps each team to mantain their own build and if a problem on the build arises, then it is something to be solved between a reduced group of people.
+
+Then both repositories can be merged togheter into an integration one by pulling from each of them.
+If there are conflicts which cannot be resolved easily, it is possible to ask the team who caused the conflict to solve it since all history is preserved.
+Then this team can clone the integration repository and merge it with its working repository.
+They can ask the person in charge to pull the changes back again.
+
+\diagrama{IndependentSubteams.jpg}{Independent Subteams workflow}
+
+\subsection{Centralized repository with integration manager}
+It is possible to have a single central repository where all developers have read access.
+Everyone has an official public version from which they can work from.
+Then, to add new change sets to the official version, an integration manager can pull the changes from each developer (or each team) to have all the changes tested and reviewed.
+When the build is good enough the integration manager can push the changes to the central repository so all developers have the new version available.
+It is also possible to have an automatic integration manager.
+This server will accept pushes, run all tests and if everything is ok it will then push this changes to the central repository.
+Otherwise it can discard the changes and signal the developer the reasons (most likely through an email).
+
+\diagrama{ResponsableIntegracion.jpg}{Centralized repository with integration manager workflow}
+
+%----------------------------------------------------------------------
+% SECTION IV: Then, why should I use it in my project?
+%----------------------------------------------------------------------
+
+%----------------------------------------------------------------------
+% SECTION VII: Conclusions
+%----------------------------------------------------------------------
+\section{CONCLUSION}
+
+%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
+%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
+% siempre desde el punto de vista "closed source" (debatible).
+%\subsection{Should I use it in my project?}
+Does everybody need these features? Speed, offline working, 
+and easyness of branching/merging are nice features even if you work simply pulling 
+and pushing changes against a central repository and not every peer out there. In some 
+projects and with some tools, the advantage of going distributed may not be clear. 
+For starters, in many closed source projects there is no need nor desire to have anything
+other than centralized repositories, and while you can use a DVCS with a centralized
+repository, there may not be enough to gain to balance the cost of changing. Distributed 
+versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
+of it, even if most of the time you can ignore most features and use just what you need 
+(even for one person proyects, Git and Mercurial may be easier to use than SVN).
+
+The general lack of maturity in the tools is also a disadvantage, since the most flexible
+way of working is the command-line interface. This makes it a bit harder to use because there 
+are many commands, and they have a lot of options and some problems may not have an intuitive 
+solution. There is more to learn and to use.
+
+If there is no need to use anything but a centralized workflow, as in Continous Integration 
+workflows, there might be little justification to use DVCS because changes are supposed to be 
+integrated quickly in the main repository.
+
+Beside these general warnings, Distributed VCS is simply more powerful and flexible than Centralized CVS.
+Everything that can be done with a centralized schema can be done in a distributed fashion, but the inverse
+is not true.
 
 \begin{thebibliography}{9}
+
+\bibitem{linusgit}
+Linus Torvalds
+\newblock \emph{Google Talk presentation on Git}
+
+\bibitem{perforceclientspec}
+Perforce documentation on ``Editing Client Specs''
+
+\newblock \emph{
+http://www.perforce.com/perforce/doc.current/manuals/p4web
+/help/editclient.html
+}
+
+\bibitem{svnmerging}
+\newblock \emph{ Git-SVN Crash Course}
+
+\newblock \emph{http://git.or.cz/course/svn.html\#merge}
+
 \bibitem{arnikar1965}  Arnikar, H.J., T.S. Rao and A. Bodne, ``A gas

### 2010-06-06 laarsample.tex
Agregado un detalle sobre tool support

@@
 
-With these DVCS, tool support and various plugins just isn't as 
-mature as systems like SVN, which are more mature and well tested. 
-Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
+Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
+For these tools most complete interface is the command line, but for the usual operations, 
+there are various visual tools to operate with the repository.
+Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
+but with Cygwin. 
+Now there is a fork of Git that ports it to windows, but the linux heritage is 
+shown and the installation includes a Bash shell. 
+Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
+but while it is simple and easy to use, it is very incomplete (for example, 
+it doesn't include the ``pull'' operation, among others).
+
 Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 

### 2010-06-06 paper.tex
Configurada la separacion entre columnas
Agregado un detalle sobre tool support

@@
 
-With these DVCS, tool support and various plugins just isn't as 
-mature as systems like SVN, which are more mature and well tested. 
-Git, in particular, is biased on Linux and doesn't really work out of the box in Windows, but works with Cygwin. 
+Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
+For these tools most complete interface is the command line, but for the usual operations, 
+there are various visual tools to operate with the repository.
+Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
+but with Cygwin. Now there is a fork of Git that ports it to windows, but 
 Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 

### 2010-06-06 laarsample.tex
necesito mergear

--- 2010-06-06 laarsample.tex
@@
 
-\section{COMPARISON}
+\section{Comparison}
+There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.
+While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS.
+One key aspect of VCS is its performance.
+It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible.
+This is not the case for all DVCS tools.
+In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
+
+This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions. 
+\diagrama{dvcs_roundup_plot_commits.png}{Check-in Dependence on Repository Growth}
+As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
+While Git takes almost nothing to do it no matter the size of the repository, others like darcs take up to 5 seconds.
+
+If you verify the size of the resulting repository on the previous simulation you would find the following:
+\diagrama{dvcs_roundup_plot_sizes.png}{Repository Size Growth}
+Doing the math you will see that the resulting checkout is about 15MBs.
+SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB.
+You might notice that Git has a "saw tooth" shape.
+That's because Git regulary optimizes its repository.
+
+The following benchmarks tested how much time it took to add a certain number of files to an empty repository. 
+\diagrama{dvcs_roundup_plot_steps1.png}{Dependance on Check-in Size}
+Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.
 
@@
 \bibitem{svnmerging}
-\newblock \emph{ Git-SVN Crash Course}
+Git-SVN Crash Test Course
+\newblock \emph{http://git.or.cz/course/svn.html\#merge}
 
-\newblock \emph{http://git.or.cz/course/svn.html\#merge}
+\bibitem{dvcsperfcomparison}
+DVCS Performance Comparison
+\newblock \emph{http://ldn.linuxfoundation.org/article/dvcs-round-one-system-rule-them-all-part-3}
 

### 2010-06-06 laarsample.tex
Cambio de PNGs por JPG

@@
 This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions. 
-\diagrama{dvcs_roundup_plot_commits.png}{Check-in Dependence on Repository Growth}
+\diagrama{dvcs_roundup_plot_commits.jpg}{Check-in Dependence on Repository Growth}
 As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
@@
 If you verify the size of the resulting repository on the previous simulation you would find the following:
-\diagrama{dvcs_roundup_plot_sizes.png}{Repository Size Growth}
+\diagrama{dvcs_roundup_plot_sizes.jpg}{Repository Size Growth}
 Doing the math you will see that the resulting checkout is about 15MBs.
@@
 The following benchmarks tested how much time it took to add a certain number of files to an empty repository. 
-\diagrama{dvcs_roundup_plot_steps1.png}{Dependance on Check-in Size}
+\diagrama{dvcs_roundup_plot_steps1.jpg}{Dependance on Check-in Size}
 Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.

### 2010-06-07 laarsample.tex
Más detalles sobre las herramientas

@@
 
-\section{Comparison}
-There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.
-While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS.
-One key aspect of VCS is its performance.
-It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible.
-This is not the case for all DVCS tools.
-In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
-
-This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions. 
-\diagrama{dvcs_roundup_plot_commits.jpg}{Check-in Dependence on Repository Growth}
-As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
-While Git takes almost nothing to do it no matter the size of the repository, others like darcs take up to 5 seconds.
-
-If you verify the size of the resulting repository on the previous simulation you would find the following:
-\diagrama{dvcs_roundup_plot_sizes.jpg}{Repository Size Growth}
-Doing the math you will see that the resulting checkout is about 15MBs.
-SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB.
-You might notice that Git has a "saw tooth" shape.
-That's because Git regulary optimizes its repository.
-
-The following benchmarks tested how much time it took to add a certain number of files to an empty repository. 
-\diagrama{dvcs_roundup_plot_steps1.jpg}{Dependance on Check-in Size}
-Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.
+\section{COMPARISON}
 
@@
 it doesn't include the ``pull'' operation, among others).
+There are many other third-party GUIs for Git, but none of them has all available operations, in those
+cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
+requires to purchase a (rather inexpensive) licence for commercial usage.
 
-Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
-to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
+Git has git-svn which allows to push and pull from svn repositories, 
 easing transitions.
@@
 \bibitem{svnmerging}
-Git-SVN Crash Test Course
+\newblock \emph{ Git-SVN Crash Course}
+
 \newblock \emph{http://git.or.cz/course/svn.html\#merge}
-
-\bibitem{dvcsperfcomparison}
-DVCS Performance Comparison
-\newblock \emph{http://ldn.linuxfoundation.org/article/dvcs-round-one-system-rule-them-all-part-3}
 

### 2010-06-07 laarsample.tex
comentario sobre tortoise-git

--- 2010-06-06 laarsample.tex
@@
 it doesn't include the ``pull'' operation, among others).
+There are many other third-party GUIs for Git, but none of them has all available operations, in those
+cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
+requires to purchase a (rather inexpensive) licence for commercial usage. An alternative is Tortoise-Git,
+which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
+Git operations.
 
-Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
-to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
+Git has git-svn which allows to push and pull from svn repositories, 
 easing transitions.

### 2010-06-07 laarsample.tex
Agregados espacios para que se vean mejor los diagramas. Agregada citation de interfaces. Comentadas citations de ejemplo.

--- 2010-06-06 laarsample.tex
@@
 This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions.
+
 \diagrama{dvcs_roundup_plot_commits.jpg}{Check-in Dependence on Repository Growth}
+
 As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
@@
 If you verify the size of the resulting repository on the previous simulation you would find the following:
+
 \diagrama{dvcs_roundup_plot_sizes.jpg}{Repository Size Growth}
+
 Doing the math you will see that the resulting checkout is about 15MBs.
@@
 The following benchmarks tested how much time it took to add a certain number of files to an empty repository.
+
 \diagrama{dvcs_roundup_plot_steps1.jpg}{Dependance on Check-in Size}
+
 Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.
@@
 there are various visual tools to operate with the repository.
+
 Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
@@
 
-Mercurial is much more portable, but some tools are also incomplete, like hg-subversion (a tool 
-to interoperate with svn). Git has git-svn which allows to push and pull from svn repositories, 
-easing transitions.
+There are many other third-party GUIs for Git, but none of them has all available operations nor are them equally mature, 
+in those cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
+requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
+is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
+Git operations. There are others GUIs but they are either very uncomplete or aren't really mature and have 
+some kind of bugs (like git-cola) \cite{interfaces}.
+
+There are some tools to interoperate with others VCS, easing transitions.
+Git in particular includes has git-svn which allows to push and pull from svn repositories.
 
@@
 
-\bibitem{arnikar1965}  Arnikar, H.J., T.S. Rao and A. Bodne, ``A gas
-chromatographic study of the kinetics of the uncatalysed esterification of
-aceticacid by ethanol,'' {\it J. Chromatog.}, {\bf 47}, 265-268 (1970).
+\bibitem{interfaces}
+Kernel.org wiki Git Interfaces Comparison
+\newblock \emph{https://git.wiki.kernel.org/index.php/Interfaces,\_frontends\_and\_tools\#Graphical\_Interfaces}
 
-\bibitem{Holland1980}  Holland, C.D., {\it Fundamentals of Multicomponent
-Distillation}, McGraw-Hill, New York (1981).
-
-\bibitem{Homatsue1977a}  Komatsue, L., ``Application of the relaxation
-method for solving reacting distillation problems,'' {\it J. Chem. Eng. Japan%
-}, {\bf 10}, 200-205 (1977a).
-
-\bibitem{Komatsue1977b}  Komatsue, L., ``A new method of convergence for
-solving reacting distillation problems,'' {\it J. Chem. Eng. Japan}, {\bf 10}%
-, 292-297 (1977b).
-
-\bibitem{Komatsue1987}  Komatsue, L. and J. Simand, ``Simulation of reactive
-distillation by the inside-outside method,'' {\it Proc. 37th Chem. Eng. Conf.%
-}, Montreal, Canada, 365-367 (1987).
+% \bibitem{arnikar1965}  Arnikar, H.J., T.S. Rao and A. Bodne, ``A gas
+% chromatographic study of the kinetics of the uncatalysed esterification of
+% aceticacid by ethanol,'' {\it J. Chromatog.}, {\bf 47}, 265-268 (1970).
+% 
+% \bibitem{Holland1980}  Holland, C.D., {\it Fundamentals of Multicomponent
+% Distillation}, McGraw-Hill, New York (1981).
+% 
+% \bibitem{Homatsue1977a}  Komatsue, L., ``Application of the relaxation
+% method for solving reacting distillation problems,'' {\it J. Chem. Eng. Japan%
+% }, {\bf 10}, 200-205 (1977a).
+% 
+% \bibitem{Komatsue1977b}  Komatsue, L., ``A new method of convergence for
+% solving reacting distillation problems,'' {\it J. Chem. Eng. Japan}, {\bf 10}%
+% , 292-297 (1977b).
+% 
+% \bibitem{Komatsue1987}  Komatsue, L. and J. Simand, ``Simulation of reactive
+% distillation by the inside-outside method,'' {\it Proc. 37th Chem. Eng. Conf.%
+% }, Montreal, Canada, 365-367 (1987).
 \end{thebibliography}

### 2010-06-07 laarsample.tex
Quité eso de que aparezca tantas veces UTN

@@
 
+%\affiliation{
+% \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+% {\ demianalonso@gmail.com} \\
+% \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+% {\ bbonanno@gmail.com} \\
+% \dag \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+% {\ nicolascalligaro@gmail.com} \\
+% \ddag \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
+% {\ nicolas.perez.santoro@gmail.com }
+% }
+
 \affiliation{
-\dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
-{\ demianalonso@gmail.com} \\
-\ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
-{\ bbonanno@gmail.com} \\
-\dag \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
-{\ nicolascalligaro@gmail.com} \\
-\ddag \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
-{\ nicolas.perez.santoro@gmail.com }
+ \dag {\ demianalonso@gmail.com} \\
+ \ddag {\ bbonanno@gmail.com} \\
+ \dag \dag  {\ nicolascalligaro@gmail.com} \\
+ \ddag \ddag  {\ nicolas.perez.santoro@gmail.com }
  }
@@
 \author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
+%\author{Demian Alonso, Bruno Bonnano, Nicol\'{a}s Calligaro and Nicol\'{a}s Perez Santoro}
 \maketitle

### 2010-06-07 laarsample.tex
Agregado comentario sobre mercurial
Agregado abstract, y en base a este reescrita parte de la introduccion

@@
 \abstract
-Estas instrucciones se presentan para ayudar a los autores a preparar su trabajo en el formato definitivo correspondiente a la materia Arquitecturas de Proyectos de IT.
-El resumen no debe exceder las 200 palabras.
+%Estas instrucciones se presentan para ayudar a los autores a preparar su trabajo en el formato definitivo 
+%correspondiente a la materia Arquitecturas de Proyectos de IT. El resumen no debe exceder las 200 palabras.
+%
+%
+Distributed Version Control Systems, as opposed to Centralized Version Control Systems, 
+are increasingly popular, being today a serious option in the election of a Version
+Control System.
+The goal of this paper is to explain what DVCS are, based on the distributed system Git, 
+and compare them to Centralized Version Control Systems,
+highlighting the differences, advantages and disadvantages of both approachs in various 
+contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
+evaluating when to use or not Distributed Version Control Systems. 
+%aprox. 60 palabras fue eso
 \endabstract
@@
 source code in a central server that everyone that can access. 
-%This central server contains all the changes and branches of the code and 
-%the users that can read the versions or commit changes have to connect 
-%to this repository. 
 Users need to access this central server to work with their VCS.
@@
 
-In this paper we're going explain what DVCS are, based on the distributed system Git, 
-and compare them to centralized Version Control Systems,
-highlighting the differences, advantages and disadvantages of both approachs in various 
-contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
-evaluating when to use or not Distributed Version Control Systems.
+As stated in the abstract, we're going to do an overview of DVCS and comparison, based on the DVCS Git. 
+First we're going to have a quick look to the history of DVCS.
+Then there is a review of the overall architecture of DVCS, and then a comparison to centralized version control systems.
+Some workflows enabled by the use of Distributed Version Control Systems are described, and finally a general evaluation of Git, DVCS in general, and whether it is or not a good idea to switch to them.
 
@@
 
+Mercurial has similar tools, incluing hg-subversion to interact with svn repositories, and Tortoise-Hg which is
+the equivalent of Tortoise-Git.
 %----------------------------------------------------------------------

### 2010-06-07 laarsample.tex
Agregados keywords. Modificada la parte de bibliografía

@@
 \keywords%
-%EndExpansion
-Por favor, incluya hasta cinco palabras clave que identifiquen en forma concreta su trabajo.
+GIT, SVN, DVCS, MERCURIAL
 \endkeywords
@@
 \bibitem{linusgit}
-Linus Torvalds
-\newblock \emph{Google Talk presentation on Git}
+Linus Torvalds \emph{Google Talk presentation on Git}
 
@@
 Perforce documentation on ``Editing Client Specs''
-
-\newblock \emph{
-http://www.perforce.com/perforce/doc.current/manuals/p4web
-/help/editclient.html
+\emph{
+http://www.perforce.com/perforce/doc.current/
+manuals/p4web/help/editclient.html
 }
@@
 Git-SVN Crash Test Course
-\newblock \emph{http://git.or.cz/course/svn.html\#merge}
+\emph{http://git.or.cz/course/svn.html\#merge}
 
@@
 DVCS Performance Comparison
-\newblock \emph{http://ldn.linuxfoundation.org/article/dvcs-round-one-system-rule-them-all-part-3}
+\emph{http://ldn.linuxfoundation.org/article/
+dvcs-round-one-system-rule-them-all-part-3}
 
@@
 Kernel.org wiki Git Interfaces Comparison
-\newblock \emph{https://git.wiki.kernel.org/index.php/Interfaces,\_frontends\_and\_tools\#Graphical\_Interfaces}
+\emph{https://git.wiki.kernel.org/index.php/
+Interfaces,\_frontends\_and\_tools\#Graphical\_Interfaces}
 

### 2010-06-08 laarsample.tex
cambio de titulo
Cambios cosméticos menores. Agregados algunos paragraph breaks necesarios. Corrreción en la parte de historia. Pushing y Pulling no son más subsecciones, quedaba mal.

@@
 
-\title{Distributed Version Control Systems}
+\title{An Overview of Distributed Version Control Systems}
 \author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
@@
 The concept of distributed repositories came up first on the commercial product 
-Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
+Sun TeamWare. Larry McVoy, who worked on Sun Teamware, later went 
 on to design BitKeeper, another commercial VCS which expanded on those ideas. 
@@
 To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
-Linus Torvalds \cite{linusgit} and Mercurial, both now mature DVCS. 
+Linus Torvalds \cite{linusgit}) and Mercurial, both now mature DVCS. 
 Other open source DVCS in use today are Bazaar, 
@@
 A DVCS has many features that makes it perfect for distributed and non-distributed developments.
-Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
+Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
 
@@
 series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+
 The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code.
@@
 Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version.
-Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag
+Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag.
 
@@
 The merging process has two possible scenarios:
+
 \emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
+
 \emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
@@
 \subsection{Pushing and pulling}
-When we want to share our work with the rest of the team we have two basic commands, 
-\emph{push} and \emph{pull}.
+When we want to share our work with the rest of the team we have two basic commands:
+%\emph{push} and \emph{pull}.
 
-\subsection{Pushing}
+\emph{Push:}
 The push process refers to taking all the changes previously selected and adding them to the repository of another peer.
 In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too.
+
 This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team.
@@
 
-\subsection{Pulling}
+\emph{Pull:} 
 Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''.

### 2010-06-08 laarsample.tex
Creada nueva seccion de comparación de DVCS porque el contenido que estaba al principio de comparison quedaba re colgado. Agregados más paragraph breaks y toqué algo en las conclusiones.

@@
 
-\section{Comparison}
-There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.
-While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS.
-One key aspect of VCS is its performance.
-It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible.
-This is not the case for all DVCS tools.
-In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
-
-This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions.
-
-\diagrama{dvcs_roundup_plot_commits.jpg}{Check-in Dependence on Repository Growth}
-
-As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
-While Git takes almost nothing to do it no matter the size of the repository, others like darcs take up to 5 seconds.
-
-If you verify the size of the resulting repository on the previous simulation you would find the following:
-
-\diagrama{dvcs_roundup_plot_sizes.jpg}{Repository Size Growth}
-
-Doing the math you will see that the resulting checkout is about 15MBs.
-SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB.
-You might notice that Git has a "saw tooth" shape.
-That's because Git regulary optimizes its repository.
-
-The following benchmarks tested how much time it took to add a certain number of files to an empty repository.
-
-\diagrama{dvcs_roundup_plot_steps1.jpg}{Dependance on Check-in Size}
-
-Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.
-
+\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
 \subsection{Commits}
@@
 %----------------------------------------------------------------------
+\section{DVCS COMPARISONS}
+There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.
+While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS.
+One key aspect of VCS is its performance.
+It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible.
+This is not the case for all DVCS tools.
+In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
+
+This benchmark simulates a linearly growing repository, being sequentially filled with 4000 files. Each file is modified five times. At the end of the test, the repository had 24,000 revisions.
+
+\diagrama{dvcs_roundup_plot_commits.jpg}{Check-in Dependence on Repository Growth}
+
+As you can see in the chart above, the time that takes to do a check-in is not constant and differs a lot from one DVCS to another.
+While Git takes almost nothing to do it no matter the size of the repository, others like darcs take up to 5 seconds.
+
+If you verify the size of the resulting repository on the previous simulation you would find the following:
+
+\diagrama{dvcs_roundup_plot_sizes.jpg}{Repository Size Growth}
+
+Doing the math you will see that the resulting checkout is about 15MBs.
+SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB.
+You might notice that Git has a "saw tooth" shape.
+That's because Git regulary optimizes its repository.
+
+The following benchmarks tested how much time it took to add a certain number of files to an empty repository.
+
+\diagrama{dvcs_roundup_plot_steps1.jpg}{Dependance on Check-in Size}
+
+Once again, Git is the fastest, taking only 300ms to add 2000 files, while SVK needed almost 23 minutes to add the same amount of files.
 
@@
 and easyness of branching/merging are nice features even if you work simply pulling 
-and pushing changes against a central repository and not every peer out there. In some 
-projects and with some tools, the advantage of going distributed may not be clear. 
-For starters, in many closed source projects there is no need nor desire to have anything
+and pushing changes against a central repository and not every peer out there.
+
+In some 
+projects and with some tools, though, the advantage of going distributed may not be clear. 
+In many closed source projects there is no need nor desire to have anything
 other than centralized repositories, and while you can use a DVCS with a centralized
-repository, there may not be enough to gain to balance the cost of changing. Distributed 
-versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
+repository, there may not be enough to gain to balance the cost of changing.
+
+Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
 of it, even if most of the time you can ignore most features and use just what you need 
@@
 
-The general lack of maturity in the tools is also a disadvantage, since the most flexible
+The general lack of completness in the tools is also a disadvantage, since the most flexible
 way of working is the command-line interface. This makes it a bit harder to use because there 
 are many commands, and they have a lot of options and some problems may not have an intuitive 
-solution. There is more to learn and to use.
+solution. There is more to learn and to use, even though some GUIs may help with these issues.
 

### 2010-06-08 laarsample.tex
Corregidas algunas cosas de redacción

@@
 Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
-but with Cygwin. 
-Now there is a fork of Git that ports it to windows, but the linux heritage is 
-shown and the installation includes a Bash shell. 
+only by using Cygwin. 
+There is now a Git fork which ports it to windows. However it still carries a linux heritage which is shown when the installation includes a Bash shell.
 Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
@@
 
-There are many other third-party GUIs for Git, but none of them has all available operations nor are them equally mature, 
-in those cases, the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
-requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
+There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
+In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
+it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
 is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 

### 2010-06-08 laarsample.tex
Agregado un párrafo con el plugin de eclipse

@@
 
+The plugin to integrate Git with Eclipse is still under major development so it only allows the most basic features to be used.
+Unfortunately, as the time this paper is being written, it is not yet mature enough to be used frequently as it usually forgets configurations.
+For instance, it cannot remember which repository to push, so each time the developer wants to push some changesets a custom repository must be specified again.
+
 There are some tools to interoperate with others VCS, easing transitions.

### 2010-06-26 laarsample.tex
Cambie el final de la introducción para que no use futuro y sea más como todos los demás paper. Agregado el uso de los \ref para crear referencias a secciones

@@
 %\input{tcilatex}
-\documentstyle[laarstyle,graphicx,fancyhdr]{article}
+%\documentstyle[laarstyle,graphicx,fancyhdr]{article}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %TCIDATA{Language=American English}
+\documentclass[a4paper,10pt]{article}
+\usepackage{graphicx}
+\usepackage{fancyhdr}
+\usepackage{laarstyle}
+\usepackage{xspace}
+
+\newcommand{\sectionReference}[1]{\hspace{-.25em}\ref{#1}\hspace{.5em}}
 
@@
 Version Control Systems traditionally track the whole history of the
-source code in a central server that everyone that can access. 
+source code in a central server that everyone can access.
 Users need to access this central server to work with their VCS.
 A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
-In these systems, there is no central server that contains the history and tracks changes,
-instead everyone has a copy of the full repository with the complete history.
+In these systems, there is no central server containing the history and tracking changes,
+instead of that has a copy of the full repository including the complete history.
 Given the lack of a centralized server they are also called De-centralized Version Control Systems.
 
-As stated in the abstract, we're going to do an overview of DVCS and comparison, based on the DVCS Git. 
-First we're going to have a quick look to the history of DVCS.
-Then there is a review of the overall architecture of DVCS, and then a comparison to centralized version control systems.
-Some workflows enabled by the use of Distributed Version Control Systems are described, and finally a general evaluation of Git, DVCS in general, and whether it is or not a good idea to switch to them.
+In section \sectionReference{DVCS HISTORY} there is a small review of DVCS's history. Later, section \sectionReference{ARCHITECTURE} covers
+all architecture elements in a DVCS. A comparison between a traditional VCS and the most recent DVCS is done on
+section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON} There is also an enumeration of possible scenarios where using a 
+DVCS might be possible and/or useful which are covered on section \sectionReference{WORKFLOWS} Finally, 
+section \sectionReference{DVCS COMPARISONS} there is an analysis on different implementation of DVCS system.
 
 \section{DVCS HISTORY}
+\label{DVCS HISTORY}
 
@@
 \section{ARCHITECTURE}
+\label{ARCHITECTURE}
 
@@
 \section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
+\label{CENTRALIZED DISTRIBUTED COMPARISON}
+
 \subsection{Commits}
@@
 \section{POSSIBLE WORKFLOWS}
+\label{WORKFLOWS}
 
@@
 \section{DVCS COMPARISONS}
+\label{DVCS COMPARISONS}
+
 There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.

### 2010-06-26 laarsample.tex
Movido un párrafo a la introducción que es donde correspondía

@@
 
-In section \sectionReference{DVCS HISTORY} there is a small review of DVCS's history. Later, section \sectionReference{ARCHITECTURE} covers
-all architecture elements in a DVCS. A comparison between a traditional VCS and the most recent DVCS is done on
-section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON} There is also an enumeration of possible scenarios where using a 
-DVCS might be possible and/or useful which are covered on section \sectionReference{WORKFLOWS} Finally, 
-section \sectionReference{DVCS COMPARISONS} there is an analysis on different implementation of DVCS system.
+This paper bases its explanations on Git but for most features there 
+are no big differences between most of these DVCS, especially between Git and Mercurial which are 
+largely similar, with most commands having the same names in both tools.
+
+In section \sectionReference{DVCS HISTORY} there is a small review of DVCS's history. Later, section
+\sectionReference{ARCHITECTURE} covers all architecture elements in a DVCS. A comparison between a traditional VCS 
+and the most recent DVCS is done on section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON} There is also an 
+enumeration of possible scenarios where using a DVCS might be possible and/or useful which are covered on section
+\sectionReference{WORKFLOWS} Finally, section \sectionReference{DVCS COMPARISONS} there is an analysis on different
+implementation of DVCS system.
 
@@
 the idea of tracking only patches and not versions.
-
-For reference, in this paper we'll base our explanations on Git but for most features there 
-are no big differences between most of these DVCS, especially between Git and Mercurial which are 
-largely similar, with most commands having the same names in both tools.
 

### 2010-07-03 laarsample.tex
Corregida la subsección de Merging

@@
 
-In section \sectionReference{DVCS HISTORY} there is a small review of DVCS's history. Later, section
+In section \sectionReference{HISTORY} there is a small review of DVCS's history. Later, section
 \sectionReference{ARCHITECTURE} covers all architecture elements in a DVCS. A comparison between a traditional VCS 
@@
 
-\section{DVCS HISTORY}
-\label{DVCS HISTORY}
+\section{HISTORY}
+\label{HISTORY}
 
@@
 
-A DVCS has many features that makes it perfect for distributed and non-distributed developments.
-Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
+% - Distributed / Architecture
+% - push-pull-commit (local commit, distributed repositories)
+% - Flexibility
+% - Changesets & patches
+% - Cherry-picking
+% - Merging
+% - Tagging & branching
+% - Trust Based Security
 
+% Descripcion de arquitectura 
+A DVCS has many features that make it perfect for distributed and non-distributed developments.
+
+Almost every feature is based on the fact that a DVCS is distributed instead of centralized.
+
+Therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
+%Arq
 \subsection{Distributed}
-The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited.
-This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes.
-It also makes the whole versioning system faster.
+The idea behind a distributed architecture means that no server has the full content of a repository. Instead of that, each 
+particular developer has a clone of the repository with the changes he has commited. 
+This allows users to version their changes in their own repository's clone while working in a offline environment.
 
+As explained in section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON}  \sectionReference{Commits} all commits are local which makes the whole versioning system faster.
+
+% Local commit
+
+% Reveer diferencia entre changes & patch. Ver bien la diferencia o juntarlos.
+%Arq
 \subsection{Change-sets}
-You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
-To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
+You could also create several other clones for every feature or bug that you want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
+To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
 
+%Arq
 \subsection{Patchs}
+% No usar you. Ver si se puede explicar mejor lo de atomic way
 The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit.
@@
 
+%
 \subsection{Flexibility}
+% Buscar reemplazo a super-set
 If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
@@
 
+%Arq | mejorar redaccion
 \subsection{Trust Based Security}
-Security on DVCS is based on the "circle of trust" model which implies that you trust only on a very specific group of people and you only pull from those people which in turn trust in their own group of people and only pull from that other group of people.
-This creates a chain of trust so that even if you don't trust some one directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.
+Security on DVCS is based on the "circle of trust" model, which implies that you trust only on a very specific group of people and you only pull from their repositories.
+They, in turn, have their own group of trust and only pull from that other group.
+This creates a chain of trust so that even if you don't trust someone directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.
 
 \subsection{Small, Coherent and Logical Commits}
-Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code.
-This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a
-series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+%
+% Dar vuelta la redacción. Tree son changesets => 
+%
+Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic, making the merging process easier by selecting only those commits that won't break your code.
+This technique of only selecting the changes that you want is called ``cherry-picking''.
+It has the advantage of using the revision tree as a series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
 
@@
 \subsection{Tagging and Branching}
-Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version.
+Most DVCSs allows the user to attach an arbitrary description to the tag so you can store the whole release announcement along with the tag of that version.
 Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag.
@@
 \emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
-The merging process\cite{svnmerging} between branches preserves all the history of 
-both branches on many DVCS tools.
+On many DVCS tools, the merging process\cite{svnmerging} between branches preserves all the history of 
+both branches.
 
 \subsection{Pushing and pulling}
-When we want to share our work with the rest of the team we have two basic commands:
+When a developer wants to share our work with the rest of the team we have two basic commands:
 %\emph{push} and \emph{pull}.
@@
 The push process refers to taking all the changes previously selected and adding them to the repository of another peer.
-In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too.
+In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is can be done against a ``central repository'' where all the team make their pushes to.
 
-This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team.
+This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of shared repositories for different parts of our project or even for different parts of the team.
 Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.
@@
 After that, the merge process combines the changes you've just downloaded with the ones on your local repository.
-You can do those two actions separately or altogether by using the ``pull'' command.
+You can do those two actions separatedly or altogether by using the ``pull'' command.
 
@@
 \subsection{Commits}
+\label{Commits}
 In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
@@
 
-Also, DVCS allow to apply a technique called ``cherry-picking'', 
+Also, DVCSs allows the ``cherry-picking'', 
 which consists of ``picking'' what changes you want to use in a version, and build 
@@
 Merging on Git between branches is greatly improved over SVN, because all the history of 
-both branches is preserved over the merges. %agregar citation
+both branches is preserved over the merges. In order to merge in a CVCS it is necessary to bring all changes from the
+branch to the head copy, make everything compile and run, and then commit those changes into the HEAD. This forces
+a single commit into the HEAD which looses the history since there is no way for the tool to know which changes belonged
+to which commits on the branch.
+%agregar citation
 
@@
 Centralized VCS also have their advantages, you don't need to have the whole history in your 
-personal repository so you can save space, for example in Perforce you can check out only a part of the 
-repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
-without getting a performance hit on some operations\cite{linusgit}.
+personal repository so you can save space. For example, in Perforce you can check out only a part of the 
+repository\cite{perforceclientspec} where as in Git this is not possible.
+% mencionar operaciones
+Git repositories can't handle millions of files without getting a performance hit on some operations\cite{linusgit}.
 
@@
 
-Systems like SVN have mature tool support and various plugins, but popular DVCS are catching up.
-For these tools most complete interface is the command line, but for the usual operations, 
+Systems like SVN have mature tool support and various plugins, but popular DVCSs are catching up.
+For these tools the most complete interface is the command line, but for the usual operations
 there are various visual tools to operate with the repository.
 
-Git, in particular, is based on Linux and originally didn't work work out of the box in Windows, 
-only by using Cygwin. 
+Git, in particular, is based on Linux and originally didn't work out of the box in Windows. \footnote{But was required Cygwin to run}
 There is now a Git fork which ports it to windows. However it still carries a linux heritage which is shown when the installation includes a Bash shell.
@@
 is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
-Git operations. There are others GUIs but they are either very uncomplete or aren't really mature and have 
+Git operations. There are others GUIs but they are either very incomplete or are not really mature and have 
 some kind of bugs (like git-cola) \cite{interfaces}.
@@
 
+% Intercalar tortoise con tortoise-git y el del svn con el svn
 Mercurial has similar tools, incluing hg-subversion to interact with svn repositories, and Tortoise-Hg which is
@@
 
+% Reveer de mover esta sección antes de la comparacion
 \section{POSSIBLE WORKFLOWS}
@@
 reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
-This also prevented them from sharing the code through a public repository, which can present some disadvantages like
+This also prevents them from sharing the code through a public repository, which can present some disadvantages like
 a third developer using code that is not yet intended for general use.
@@
 The classic workflow where there is one central server which has the whole project is also available.
-In this case all developers has access to the server and can pull and push changes from it.
-The main advantages is that any developer can share changes among other developer without needing to use the central server.
-However once a piece of code is considered finished it should be pushed to this server.
+In this case all developers have access to the server and can pull and push changes from it.
+The main advantages is that any developer can share changes with other developers without being forced to use a central server.
+However, once a piece of code is considered finished it should be pushed to this server.
 
@@
 There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments.
-While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS.
-One key aspect of VCS is its performance.
+While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN which is probably the most widely used VCS.
+
+One key aspect of a VCS is its performance.
 It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible.
 This is not the case for all DVCS tools.
-In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.
+In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCSs.
 
@@
 
+% Reveer saw tooth a ver si se dice así de posta
 Doing the math you will see that the resulting checkout is about 15MBs.
@@
 
-The following benchmarks tested how much time it took to add a certain number of files to an empty repository.
+The following benchmarks test how much time it takes to add a certain number of files to an empty repository.
 
@@
 
-In some 
-projects and with some tools, though, the advantage of going distributed may not be clear. 
+In some projects and with some tools, though, the advantage of going distributed may not be clear. 
 In many closed source projects there is no need nor desire to have anything
-other than centralized repositories, and while you can use a DVCS with a centralized
-repository, there may not be enough to gain to balance the cost of changing.
+other than centralized repositories, and while you can use a DVCS with centralized
+workflow, there may not be enough to gain to balance the cost of changing.
 
+% Re-redactar el paréntesis que está confuso
 Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
@@
 
-Beside these general warnings, Distributed VCS is simply more powerful and flexible than Centralized CVS.
+Beside these general warnings, Distributed VCS is simply more powerful and flexible than Centralized VCS.
 Everything that can be done with a centralized schema can be done in a distributed fashion, but the inverse
@@
 
+% Ver porque no aparecen los números en las citas!
 \begin{thebibliography}{9}

### 2010-07-03 laarsample.tex
Sawtooth está bien :)
Ajustada la sección Small, Coherent and Logica commits

@@
 \subsection{Small, Coherent and Logical Commits}
-%
-% Dar vuelta la redacción. Tree son changesets => 
-%
-Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic, making the merging process easier by selecting only those commits that won't break your code.
-This technique of only selecting the changes that you want is called ``cherry-picking''.
-It has the advantage of using the revision tree as a series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+A revision tree is composed of a series of \emph{changesets} or \emph{patches} instead of just a series of static versions. A changeset or patch
+can be as little as a very specific piece of code inside a much bigger and already modified file. Selecting only portions of the whole modifications
+allows the user to make smaller commits which can describe change sepparatedly. It would then be easier to make a merge since you can select
+only a commit that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking''.
 
@@
 
-% Reveer saw tooth a ver si se dice así de posta
 Doing the math you will see that the resulting checkout is about 15MBs.
 SVK needs almost 1.8 GB to store that repository, while the rest of them needs less that 150MB.
-You might notice that Git has a "saw tooth" shape.
+You might notice that Git has a sawtooth shape.
 That's because Git regulary optimizes its repository.

### 2010-07-03 laarsample.tex
Mejorada la redacción de Patchs

@@
 \subsection{Patchs}
-% No usar you. Ver si se puede explicar mejor lo de atomic way
-The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit.
-You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.
+The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
+which of the local changes goes into the commit.
+Different parts of a single file can be selected to join the commit and which ones doesn't.
+Only those selected parts will conform the commit.
+The ability to select only parts of all the modifications makes the commits very atomic.
 
@@
 If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
-This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.
+This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all  a super-set of a centralized CVS although in really it is not.
 

### 2010-07-03 laarsample.tex
Reemplazada la palabra super-set

@@
 
-%Arq
 \subsection{Patchs}
@@
 
-%
 \subsection{Flexibility}
-% Buscar reemplazo a super-set
 If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
-This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all  a super-set of a centralized CVS although in really it is not.
+This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all features of a centralized CVS although in really it is not.
 

### 2010-07-03 laarsample.tex
reubicada la seccion Possible Workflows
Pequeño fix en la sección Tool Support
Mejorada la redacción de la sección Trust Based Securirty

@@
 
-%Arq | mejorar redaccion
 \subsection{Trust Based Security}
-Security on DVCS is based on the "circle of trust" model, which implies that you trust only on a very specific group of people and you only pull from their repositories.
-They, in turn, have their own group of trust and only pull from that other group.
-This creates a chain of trust so that even if you don't trust someone directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.
+Security on DVCS is based on the "circle of trust" model. This model proposes that a developer should only pull changes from a specific group of people
+in which she trusts. This people have, at the same time, their own group of trust from which they pull. Following this chain any change could scalate
+to any repository, provided that someone trustworthy has reviewed it.
 
@@
 
-\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
-\label{CENTRALIZED DISTRIBUTED COMPARISON}
-
-\subsection{Commits}
-\label{Commits}
-In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
-Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
-DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.
-
-Also, DVCSs allows the ``cherry-picking'', 
-which consists of ``picking'' what changes you want to use in a version, and build 
-a new version containing only those changes. This way the revision tree is seen as a 
-series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
-
-\subsection{Merging}
-Merging on Git between branches is greatly improved over SVN, because all the history of 
-both branches is preserved over the merges. In order to merge in a CVCS it is necessary to bring all changes from the
-branch to the head copy, make everything compile and run, and then commit those changes into the HEAD. This forces
-a single commit into the HEAD which looses the history since there is no way for the tool to know which changes belonged
-to which commits on the branch.
-%agregar citation
-
-\subsection{Sharing changes}
-If you work simply pulling and pushing against a central repository, those operations do look 
-very much like the operations idea of check out and check in in a centralized VCS, 
-but that's the only way of sharing changes in a centralized VCS.
-In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
-read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
-
-\subsection{Repository Size}
-
-Centralized VCS also have their advantages, you don't need to have the whole history in your 
-personal repository so you can save space. For example, in Perforce you can check out only a part of the 
-repository\cite{perforceclientspec} where as in Git this is not possible.
-% mencionar operaciones
-Git repositories can't handle millions of files without getting a performance hit on some operations\cite{linusgit}.
-
-\subsection{Tool support}
-%the idea here is to explain a bit the state of the art in the toolchain support
-%eclipse plugins, tortoisegit 'n tortoisehg, etc.
-
-Systems like SVN have mature tool support and various plugins, but popular DVCSs are catching up.
-For these tools the most complete interface is the command line, but for the usual operations
-there are various visual tools to operate with the repository.
-
-Git, in particular, is based on Linux and originally didn't work out of the box in Windows. \footnote{But was required Cygwin to run}
-There is now a Git fork which ports it to windows. However it still carries a linux heritage which is shown when the installation includes a Bash shell.
-Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
-but while it is simple and easy to use, it is very incomplete (for example, 
-it doesn't include the ``pull'' operation, among others).
-
-There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
-In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
-it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
-is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
-Git operations. There are others GUIs but they are either very incomplete or are not really mature and have 
-some kind of bugs (like git-cola) \cite{interfaces}.
-
-The plugin to integrate Git with Eclipse is still under major development so it only allows the most basic features to be used.
-Unfortunately, as the time this paper is being written, it is not yet mature enough to be used frequently as it usually forgets configurations.
-For instance, it cannot remember which repository to push, so each time the developer wants to push some changesets a custom repository must be specified again.
-
-There are some tools to interoperate with others VCS, easing transitions.
-Git in particular includes has git-svn which allows to push and pull from svn repositories.
-
-% Intercalar tortoise con tortoise-git y el del svn con el svn
-Mercurial has similar tools, incluing hg-subversion to interact with svn repositories, and Tortoise-Hg which is
-the equivalent of Tortoise-Git.
 %----------------------------------------------------------------------
 
-% Reveer de mover esta sección antes de la comparacion
 \section{POSSIBLE WORKFLOWS}
@@
 \diagrama{ResponsableIntegracion.jpg}{Centralized repository with integration manager workflow}
+
+\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
+\label{CENTRALIZED DISTRIBUTED COMPARISON}
+
+\subsection{Commits}
+\label{Commits}
+In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
+Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
+DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.
+
+Also, DVCSs allows the ``cherry-picking'', 
+which consists of ``picking'' what changes you want to use in a version, and build 
+a new version containing only those changes. This way the revision tree is seen as a 
+series of \emph{changesets} or \emph{patches} instead of just a series of static versions.
+
+\subsection{Merging}
+Merging on Git between branches is greatly improved over SVN, because all the history of 
+both branches is preserved over the merges. In order to merge in a CVCS it is necessary to bring all changes from the
+branch to the head copy, make everything compile and run, and then commit those changes into the HEAD. This forces
+a single commit into the HEAD which looses the history since there is no way for the tool to know which changes belonged
+to which commits on the branch.
+%agregar citation
+
+\subsection{Sharing changes}
+If you work simply pulling and pushing against a central repository, those operations do look 
+very much like the operations idea of check out and check in in a centralized VCS, 
+but that's the only way of sharing changes in a centralized VCS.
+In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
+read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.
+
+\subsection{Repository Size}
+
+Centralized VCS also have their advantages, you don't need to have the whole history in your 
+personal repository so you can save space. For example, in Perforce you can check out only a part of the 
+repository\cite{perforceclientspec} where as in Git this is not possible.
+% mencionar operaciones
+Git repositories can't handle millions of files without getting a performance hit on some operations\cite{linusgit}.
+
+\subsection{Tool support}
+%the idea here is to explain a bit the state of the art in the toolchain support
+%eclipse plugins, tortoisegit 'n tortoisehg, etc.
+
+Systems like SVN have mature tool support and various plugins, but popular DVCSs are catching up.
+For these tools the most complete interface is the command line, but for the usual operations
+there are various visual tools to operate with the repository.
+
+Git, in particular, is based on Linux and originally didn't work out of the box in Windows. \footnote{But was required Cygwin to run}
+There is now a Git fork which ports it to windows. However it still carries a linux heritage which is shown when the installation includes a Bash shell.
+Git also includes a portable GUI written in Tk, invoked with command ``git gui'' 
+but while it is simple and easy to use, it is very incomplete (for example, 
+it doesn't include the ``pull'' operation, among others).
+
+There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
+In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
+it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
+is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
+Git operations. There is also a Tortoise-Hg to work with Mercurial DVCS.
+There are others GUIs but they are either very incomplete or are not really mature and have 
+some kind of bugs (like git-cola) \cite{interfaces}.
+
+The plugin to integrate Git with Eclipse is still under major development so it only allows the most basic features to be used.
+Unfortunately, as the time this paper is being written, it is not yet mature enough to be used frequently as it usually forgets configurations.
+For instance, it cannot remember which repository to push, so each time the developer wants to push some changesets a custom repository must be specified again.
+
+There are some tools to interoperate with others VCS, easing transitions.
+Git in particular includes has git-svn which allows to push and pull from svn repositories. This is also available for Mercurial DVCS
+with the hg-subversion project.
 

### 2010-07-04 laarsample.tex
Mejorado el punto Architecture.Distributed

@@
 % SECTION II: Architecture
-%----------------------------------------------------------------------
+1%----------------------------------------------------------------------
 \section{ARCHITECTURE}
@@
 
-% - Distributed / Architecture
-% - push-pull-commit (local commit, distributed repositories)
-% - Flexibility
-% - Changesets & patches
-% - Cherry-picking
-% - Merging
-% - Tagging & branching
-% - Trust Based Security
-
-% Descripcion de arquitectura 
-A DVCS has many features that make it perfect for distributed and non-distributed developments.
-
-Almost every feature is based on the fact that a DVCS is distributed instead of centralized.
-
-Therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
-%Arq
 \subsection{Distributed}
@@
 particular developer has a clone of the repository with the changes he has commited. 
-This allows users to version their changes in their own repository's clone while working in a offline environment.
+This allows users to version their changes in their own repository's clone while working in a offline environment. This means that the developer's commit
+will, at first, remain on its local clone where no one else can see them.
+This makes the whole versioning system faster and is explained in section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON}  \sectionReference{Commits}
 
-As explained in section \sectionReference{CENTRALIZED DISTRIBUTED COMPARISON}  \sectionReference{Commits} all commits are local which makes the whole versioning system faster.
-
-% Local commit
-
-% Reveer diferencia entre changes & patch. Ver bien la diferencia o juntarlos.
-%Arq
-\subsection{Change-sets}
-You could also create several other clones for every feature or bug that you want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
-To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
-
-\subsection{Patchs}
-The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
-which of the local changes goes into the commit.
-Different parts of a single file can be selected to join the commit and which ones doesn't.
-Only those selected parts will conform the commit.
-The ability to select only parts of all the modifications makes the commits very atomic.
-
-\subsection{Flexibility}
-If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
-This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all features of a centralized CVS although in really it is not.
-
-\subsection{Trust Based Security}
-Security on DVCS is based on the "circle of trust" model. This model proposes that a developer should only pull changes from a specific group of people
-in which she trusts. This people have, at the same time, their own group of trust from which they pull. Following this chain any change could scalate
-to any repository, provided that someone trustworthy has reviewed it.
-
-\subsection{Small, Coherent and Logical Commits}
-A revision tree is composed of a series of \emph{changesets} or \emph{patches} instead of just a series of static versions. A changeset or patch
-can be as little as a very specific piece of code inside a much bigger and already modified file. Selecting only portions of the whole modifications
-allows the user to make smaller commits which can describe change sepparatedly. It would then be easier to make a merge since you can select
-only a commit that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking''.
-
-The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code.
-Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.
-
-\subsection{Tagging and Branching}
-Most DVCSs allows the user to attach an arbitrary description to the tag so you can store the whole release announcement along with the tag of that version.
-Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag.
-
-\subsection{Merging}
-The merging process has two possible scenarios:
-
-\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
-
-\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
-On many DVCS tools, the merging process\cite{svnmerging} between branches preserves all the history of 
-both branches.
+Then the developers can share their changes by pushing them into someone else's repository or by pulling changes from them.
+Therefore, if you work distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
 
@@
 You can do those two actions separatedly or altogether by using the ``pull'' command.
+
+\subsection{Flexibility}
+If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository.
+This shows how flexible a DVCS is, to the point of being able to describe it as something that contains all features of a centralized CVS although in really it is not.
+
+% Reveer diferencia entre changes & patch. Ver bien la diferencia o juntarlos.
+%Arq
+\subsection{Change-sets}
+You could also create several other clones for every feature or bug that you want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
+To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
+
+\subsection{Patchs}
+The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
+which of the local changes goes into the commit.
+Different parts of a single file can be selected to join the commit and which ones doesn't.
+Only those selected parts will conform the commit.
+The ability to select only parts of all the modifications makes the commits very atomic.
+
+\subsection{Small, Coherent and Logical Commits}
+A revision tree is composed of a series of \emph{changesets} or \emph{patches} instead of just a series of static versions. A changeset or patch
+can be as little as a very specific piece of code inside a much bigger and already modified file. Selecting only portions of the whole modifications
+allows the user to make smaller commits which can describe change sepparatedly. It would then be easier to make a merge since you can select
+only a commit that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking''.
+
+The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code.
+Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.
+
+\subsection{Merging}
+The merging process has two possible scenarios:
+
+\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
+
+\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
+On many DVCS tools, the merging process\cite{svnmerging} between branches preserves all the history of 
+both branches.
+
+\subsection{Tagging and Branching}
+Most DVCSs allows the user to attach an arbitrary description to the tag so you can store the whole release announcement along with the tag of that version.
+Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag.
+
+\subsection{Trust Based Security}
+Security on DVCS is based on the "circle of trust" model. This model proposes that a developer should only pull changes from a specific group of people
+in which she trusts. This people have, at the same time, their own group of trust from which they pull. Following this chain any change could scalate
+to any repository, provided that someone trustworthy has reviewed it.
 

### 2010-07-04 laarsample.tex
Fusionadas las secciones Change-sets y Patchs

@@
 
-% Reveer diferencia entre changes & patch. Ver bien la diferencia o juntarlos.
-%Arq
 \subsection{Change-sets}
-You could also create several other clones for every feature or bug that you want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone.
+It is very easy to create several other clones for every feature or bug that the developer wants to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to the local clone.
 To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.
 
-\subsection{Patchs}
-The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
-which of the local changes goes into the commit.
+To make better fine grain changesets, it is possible to select which of the developer's local changes goes into the commit.
 Different parts of a single file can be selected to join the commit and which ones doesn't. 
-Only those selected parts will conform the commit.
-The ability to select only parts of all the modifications makes the commits very atomic.
+Only those selected parts will conform the commit. The ability to select only parts of all the modifications makes the commits very atomic.
 

### 2010-07-04 laarsample.tex
Quitados un par de you

@@
 Then the developers can share their changes by pushing them into someone else's repository or by pulling changes from them.
-Therefore, if you work distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
+Therefore, if the work environment is distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.
 
@@
 The fetch command takes the changes from a peer's repository and copies them to the local repository.
-After that, the merge process combines the changes you've just downloaded with the ones on your local repository.
-You can do those two actions separatedly or altogether by using the ``pull'' command.
+After that, the merge process combines the changes that have been just pulled with the ones on the local repository.
+Those two actions can be executed separatedly or altogether by using the ``pull'' command.
 

### 2010-09-08 laarsample.tex
Corregida la redaccion de un parrafo de la conclusion

@@
 % SECTION II: Architecture
-1%----------------------------------------------------------------------
+%----------------------------------------------------------------------
 \section{ARCHITECTURE}
@@
 Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
-of it, even if most of the time you can ignore most features and use just what you need 
-(even for one person proyects, Git and Mercurial may be easier to use than SVN).
+of it, even if most of the time you can ignore most features and use just what you need. However for one person proyects, 
+Git and Mercurial might be easier to use than SVN.
 
